### 2022-07-01 README.Rmd
Initial commit

---
output: github_document
---

```{r library, warning=FALSE, message = FALSE}
#load library
library(dplyr)
library(reshape2)
library(openxlsx)
library(car)
library(ggplot2)
library(hrbrthemes)
library(viridis)
library(ggpattern)

#load data 
load("kcmo2019_2020.rdata")
```

```{r clean, warning=FALSE, message = FALSE}
# create year+month var
dat$date = dat$CREATEYR*100 +dat$CREATEMO

dat$date = as.Date(as.character(dat$date*100+1),"%Y%m%d")

# create covid related calls 
dat = dat %>%
  mutate(

    covid = as.numeric(grepl("covid",tolower(description))|
                         grepl("corona",tolower(description))|
                         grepl("pandemic",tolower(description))|
                         grepl("virus",tolower(description))|
                         grepl("positive",tolower(description))
    ),

    mask = as.numeric(grepl("mask",tolower(description))|
                        grepl("face cover",tolower(description))|
                        grepl("ppe ",tolower(description))|
                        grepl("coverings",tolower(description))
    ),

    sdistance = as.numeric(grepl("social",tolower(description))|
                             grepl("distanc",tolower(description))|
                             grepl("6 feet",tolower(description))|
                             grepl("quarantine",tolower(description))|
                             grepl("stay at home",tolower(description))|
                             grepl("gathering",tolower(description))
    ),

    essential = as.numeric(grepl("essential",tolower(description))|
                             grepl("still open",tolower(description))|
                             grepl("open for business",tolower(description))|
                             grepl("open and operating",tolower(description))|
                             grepl("still operating",tolower(description))
    ),

    allcovid = as.numeric((covid==1|mask==1|sdistance==1|essential==1) & season == "COVID-warm")
  )
```

Aggregate Trends

Call Volumes

```{r vol, warning=FALSE, message = FALSE,fig.width=8}
dat %>% 
  group_by(date,CREATEYR,CREATEMO,allcovid) %>%
  count() %>% 
  filter(CREATEMO %in% 3:8) %>%
  mutate(CREATEYR = as.factor(CREATEYR),allcovid = as.factor(allcovid) )%>%
  ggplot(aes(x = CREATEMO, y = n,  group = CREATEYR, fill = CREATEYR))+
  geom_col_pattern(aes(pattern = reorder(allcovid,n)),position = position_dodge(),
                   col="black",width = 0.8)+
  scale_fill_manual(values = c("dodgerblue4","green3"))+
  scale_pattern_manual(values=c("stripe","none"))+
  scale_x_continuous(breaks = 3:8)+
  scale_y_continuous(labels =scales::comma)+
  labs(y = "Requests Volume",
       x = "Month",
       fill = "Year",
       pattern = "Covid-Related"
       )+
  theme_bw()
```

Call Volumes by Request Types

```{r vol_cat, warning=FALSE, message = FALSE,fig.width=15,fig.height=8}
# changes in request volume after covid by categories 
diff = dat %>% 
  filter(CATEGORY != "Data Not Available") %>%
  filter(CREATEMO %in% 3:8) %>%
  group_by(CREATEYR,CATEGORY) %>%
  count() %>% 
  dcast(CATEGORY~CREATEYR) %>% 
  mutate(diff = `2020`-`2019`,
         diff_pchg = `2020`/`2019` )

# plot request volume by categories
dat %>% 
  filter(CATEGORY != "Data Not Available") %>%
  filter(CREATEMO %in% 3:8) %>%
  group_by(CREATEYR,allcovid,CATEGORY) %>%
  count() %>% 
  left_join(diff)%>%
  mutate(CREATEYR = as.factor(CREATEYR),allcovid = as.factor(allcovid) )%>%
  ggplot(aes(x = CREATEYR, y = n,  group = reorder(CREATEYR,n), fill = CREATEYR))+
  geom_col_pattern(aes(pattern = reorder(allcovid,n)),#position = position_dodge(),
                   col="black",width = 0.8)+
  facet_wrap(~reorder(CATEGORY,-diff_pchg), scale = "free_y", ncol = 5)+
  scale_fill_manual(values = c("dodgerblue4","green3"))+
  scale_pattern_manual(values=c("stripe","none"))+
  scale_y_continuous(labels =scales::comma)+
  labs(x = "Requests Volume",
       y = "Category",
       fill = "Year",
       pattern = "Covid-Related"
       )+
  theme_bw()
```

Discussion

Categories vs Departments

```{r cate_dept, fig.height=8,fig.width=8}
dat %>%
  filter(CATEGORY != "Data Not Available") %>%
  filter(CREATEMO %in% 3:8) %>%
  group_by(CATEGORY, DEPT) %>%
  count() %>%
  left_join(diff)%>%
  mutate(selected = CATEGORY %in% c("Public Health","Public Safety","Parks & Recreation"))%>%
  ggplot(aes(x = reorder(CATEGORY,-diff_pchg), y = DEPT, fill = n, col = selected))+
  geom_tile(lwd=1.5)+
  scale_x_discrete(guide = guide_axis(angle = 90))+
  scale_color_manual(values=c("white","red"))+
  labs(
    y = "Department",
    x = "Category",
    fill = "Request Volume",
    col = "Selected Catgories"
  )+
  theme_bw()
```

911 trends 
```{r 911}
dat911 = read.csv("kcmo 911 volume - data.csv")

```

### 2022-07-01 kcmo_311_coviddid.R

@@ -1,0 +1,277 @@
+# library(dplyr)
+# library(reshape2)
+# library(openxlsx)
+# library(car)
+# 
+# #change directory
+# setwd("C:/Users/bebut/Downloads")
+# 
+# #######################################
+# # Data Cleaning 
+# #######################################
+# 
+# #load data
+# raw_a = read.xlsx("Group3-311DataPreCOVID-Warm Season.xlsx")[,-31] %>% mutate(season = "PreCOVID-Warm")
+# raw_b = read.xlsx("Group2-311DataPreCOVID-Cold Season.xlsx")[,-31] %>% mutate(season = "PreCOVID-COld")
+# raw_c = read.xlsx("Group1-311DataDuringCOVID.xlsx")[,-31] %>% mutate(season = "COVID-warm")
+# 
+# raw = rbind(raw_a,raw_b) 
+# raw = rbind(raw,raw_c)
+# 
+# sec = read.xlsx("SocioEconomic.xlsx")
+# 
+# rm(raw_a)
+# rm(raw_b)
+# rm(raw_c)
+# 
+# #merge 
+# inc = sec %>% select(NEIGH = NBH_NAME, Income.Level)
+# dat = left_join(raw,inc, by="NEIGH")
+# dat$Income.Level[dat$NEIGH == "Central Blue Valley and Park Tower Gardens"] = "L"      
+# 
+# #drop na neighborhood, income level, source, category, day to close 
+# dat = dat %>% filter(!(is.na(NEIGH)|is.na(Income.Level)|is.na(SOURCE)|is.na(CATEGORY)|is.na(DAYTOCLOSE)))
+# 
+# #drop sept 2020 for low count 
+# dat = dat %>% filter(!(CREATEYR==2020 & CREATEMO == 9))
+# 
+# #weight 
+# dat$weight = 1
+# 
+# #######################################
+# # Scraping 
+# #######################################
+# 
+# diseasecontrol = dat %>% filter(REQTYPE == "Public Health-Disease Control-All")
+# 
+# library(rvest)
+# 
+# diseasecontrol$resol_sum = NA
+# diseasecontrol$resol_des = NA
+# 
+# diseasecontrol$resol_sum2 = NA
+# diseasecontrol$resol_des2 = NA
+# 
+# for (i in  1:length(diseasecontrol$CASEURL)){
+#   
+#   tryCatch({
[…]

### 2022-07-02 README.Rmd
Update

@@
 ---
+title: "Did COVID-19 Induce A Strenuous Effect on the 311 Non-Emergency Services System?"
 output: github_document
@@
 
-#load data 
+#load 311 data 
 load("kcmo2019_2020.rdata")
+
+#load 911 data
+dat911 = read.csv("kcmo 911 volume - data.csv")
+
+#covid cases by zipcode as of january 15, 2022
+zip_covid = read.csv("COVID-19_Data_by_ZIP_Code.csv") 
+zip_covid = zip_covid %>% dplyr::select(ZipCode,Cases,Total.Residents.Tested) %>% mutate(ZIP = ZipCode,rate = Cases/Total.Residents.Tested ) %>% dplyr::select(ZIP, rate)
+
 ```
@@
 ```
+```{r rep_cat, warning=FALSE, message = FALSE,fig.height = 3,fig.width=8}
+# plot response time by categories
+dat %>% 
+  filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
+  filter(CREATEMO %in% 3:8) %>%
+  filter(allcovid==0) %>%
+  left_join(diff)%>%
+  mutate(CREATEYR = as.factor(CREATEYR))%>%
+  ggplot(aes(x = CREATEYR, y = DAYTOCLOSE, fill = CREATEYR))+
+  geom_boxplot(outlier.shape = NA,show.legend = FALSE)+
+  facet_wrap(~reorder(CATEGORY,-diff_pchg), ncol = 5)+
+  scale_fill_manual(values = c("dodgerblue4","green3"))+
+  ylim(c(0,80))+
+  labs(x = "",
+       y = "Reponse Time",
+       fill = "Year",
+       pattern = "Covid-Related"
+       )+
+  theme_bw()
+```
+
+Zip Code Variation
+
+```{r zipdata}
+# yoy change in days to close
+zip_dtc = dat %>% 
+  filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
+  filter(CREATEMO %in% 3:8) %>%
+  group_by(CREATEYR,CATEGORY, ZIP) %>%
+  summarize(daytoclose = mean(DAYTOCLOSE,na.rm=T)) %>%
+  dcast(CATEGORY + ZIP ~ CREATEYR) %>% 
+  mutate(daytoclose_diff = `2020`-`2019`)%>% rename(daytoclose_2020 = `2020`,daytoclose_2019=`2019`)
+
+# yoy change in volume
+zip_n = dat %>% 
+  filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
+  filter(CREATEMO %in% 3:8) %>%
+  group_by(CREATEYR,CATEGORY, ZIP) %>%
+  summarize(n = n()) %>%
+  dcast(CATEGORY + ZIP ~ CREATEYR) %>% 
+  mutate(n_diff = `2020`-`2019`)  %>% rename(n_2020 = `2020`,n_2019=`2019`)
+
+#merge data 
+zip = zip_dtc %>% left_join(zip_n) %>%
+  left_join(zip_covid)
+
+```
+```{r zip_vol, fig.height = 3,fig.width=8}
+#scatterplot
+zip %>% 
+  ggplot(aes(y = n_diff, x = rate, size = n_2019, col = ZIP))+
+  geom_point()+
+  geom_smooth(method=lm)+
+  facet_wrap(~CATEGORY, scale = "free_y")+
+  theme_bw()+
+  theme(legend.position = "none")
+```
+```{r zip_dtc, fig.height = 3,fig.width=8}
+#scatterplot
+zip %>% 
+  ggplot(aes(y = daytoclose_diff, x = rate, size = daytoclose_2019, col = ZIP))+
+  geom_point()+
+  geom_smooth(method=lm)+
+  facet_wrap(~CATEGORY, scale = "free_y")+
+  theme_bw()+
+  theme(legend.position = "none")
+```
+
+```{r zip_dtc, fig.height = 3,fig.width=8}
+#scatterplot
+zip %>% 
+  ggplot(aes(y = daytoclose_diff, x = n_diff, size = n_2019, col = ZIP))+
+  geom_point()+
+  geom_smooth(method=lm)+
+  facet_wrap(~CATEGORY, scale = "free")+
+  theme_bw()+
+  theme(legend.position = "none")
+```
 
@@
 911 trends 
-```{r 911}
-dat911 = read.csv("kcmo 911 volume - data.csv")
+```{r vol911}
 
+dat911 %>% 
+  filter(month %in% 3:8) %>%
+  mutate(year = as.factor(year)) %>%
+  select(year, month, 
+         kcmo_fire_vol,kcmo_fire_vol_911,kcmo_fire_vol_nonemergency,
+         kcmo_pd_vol,kcmo_pd_vol_911,kcmo_pd_vol_nonemergency) %>%
+  melt(id.vars=c("year","month")) %>%
+  ggplot(aes(x = year, y = value, group = year, fill = year)) + 
+  geom_boxplot(show.legend=FALSE)+
+  facet_wrap(~variable,scale="free_y")+
+  scale_fill_manual(values = c("dodgerblue4","green3"))+
+  #scale_x_continuous(breaks = 3:8)+
+  scale_y_continuous(labels =scales::comma)+
+  labs(y = "911 Volume",
+       x = "Month",
+       fill = "Year"
+       )+
+  theme_bw()
 ```
+
+```{r ringtime911}
+
+dat911 %>% 
+  filter(month %in% 3:8) %>%
+  mutate(year = as.factor(year)) %>%
+  select(year, month, 
+         kcmo_fire_pct_answered_15s,kcmo_fire_pct_answered_20s,kcmo_fire_pct_answered_40s,
+         kcmo_pd_pct_answered_15s,kcmo_pd_pct_answered_20s,kcmo_pd_pct_answered_40s) %>%
+  melt(id.vars=c("year","month")) %>%
+  ggplot(aes(x = year, y = value, group = year, fill = year)) + 
+  geom_boxplot(show.legend=FALSE)+
+  facet_wrap(~variable,scale="free_y")+
+  scale_fill_manual(values = c("dodgerblue4","green3"))+
+  labs(y = "911 Ringtime Range",
+       x = "",
+       fill = "Year"
+       )+
+  theme_bw()
+```

### 2022-07-04 README.Rmd
update

@@
 library(ggpattern)
+library(plm)
+library(haven)
+library(texreg)
+library(lfe)
 
@@
   geom_boxplot(outlier.shape = NA,show.legend = FALSE)+
-  facet_wrap(~reorder(CATEGORY,-diff_pchg), ncol = 5)+
+  facet_wrap(~reorder(CATEGORY,-diff_pchg), ncol = 3,scale="free")+
   scale_fill_manual(values = c("dodgerblue4","green3"))+
@@
   dcast(CATEGORY + ZIP ~ CREATEYR) %>% 
-  mutate(n_diff = `2020`-`2019`)  %>% rename(n_2020 = `2020`,n_2019=`2019`)
+  mutate(n_diff = `2020`-`2019`,
+         n_pchg = (`2020` / `2019`-1)*100)  %>% rename(n_2020 = `2020`,n_2019=`2019`)
 
@@
 ```
+
 ```{r zip_vol, fig.height = 3,fig.width=8}
-#scatterplot
-zip %>% 
-  ggplot(aes(y = n_diff, x = rate, size = n_2019, col = ZIP))+
-  geom_point()+
-  geom_smooth(method=lm)+
-  facet_wrap(~CATEGORY, scale = "free_y")+
-  theme_bw()+
-  theme(legend.position = "none")
+# #scatterplot
+# zip %>% 
+#   ggplot(aes(y = n_diff, x = rate, size = n_2019, col = ZIP))+
+#   geom_point()+
+#   geom_smooth(method=lm)+
+#   facet_wrap(~CATEGORY, scale = "free_y")+
+#   theme_bw()+
+#   theme(legend.position = "none")
 ```
+
 ```{r zip_dtc, fig.height = 3,fig.width=8}
-#scatterplot
+#scatter plot
 zip %>% 
@@
 
-```{r zip_dtc, fig.height = 3,fig.width=8}
-#scatterplot
-zip %>% 
-  ggplot(aes(y = daytoclose_diff, x = n_diff, size = n_2019, col = ZIP))+
-  geom_point()+
-  geom_smooth(method=lm)+
-  facet_wrap(~CATEGORY, scale = "free")+
-  theme_bw()+
-  theme(legend.position = "none")
+```{r zip_dtc2, fig.height = 3,fig.width=8}
+# #scatterplot
+# zip %>% 
+#   ggplot(aes(y = daytoclose_diff, x = n_diff, size = n_2019, col = ZIP))+
+#   geom_point()+
+#   geom_smooth(method=lm)+
+#   facet_wrap(~CATEGORY, scale = "free")+
+#   theme_bw()+
+#   theme(legend.position = "none")
+```
+
+```{r}
+# covid related request by zip code 
+zip_covid_311 = dat %>% group_by(ZIP) %>% 
+  summarise(n_allcovid = sum(allcovid))
+
+# create data for request level reg
+dat_reg = dat %>% 
+  left_join(zip_covid) %>%
+  left_join(zip_covid_311) %>% 
+  mutate(after = as.numeric(season == "COVID-warm"),
+         rate = rate*100) %>% 
+  filter(allcovid==0) %>% 
+  mutate(did = rate*after,
+         did2 = n_allcovid*after)
+
+```
+
+```{r tab1}
+#ols 
+reg_ols = (lm(data= dat_reg, DAYTOCLOSE~did + rate + after))
+#fe: rate + after
+reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~did|rate+after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~did|rate+factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
+          omit.coef = "after|rate|Intercept", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.coef.names = "DiD effect"
+          )
+
+```
+
+```{r tab2}
+#ols 
+reg_ols = (lm(data= dat_reg[dat_reg$CATEGORY == "Public Health",], DAYTOCLOSE~did + rate + after))
+#fe: rate + after
+reg_fe_a = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Health",],DAYTOCLOSE~did|rate+after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Health",],DAYTOCLOSE~did|rate+factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
+          omit.coef = "after|rate|Intercept", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.coef.names = "DiD effect"
+          )
+
+```
+
+```{r tab3}
+#ols 
+reg_ols = (lm(data= dat_reg[dat_reg$CATEGORY == "Public Safety",], DAYTOCLOSE~did + rate + after))
+#fe: rate + after
+reg_fe_a = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Safety",],DAYTOCLOSE~did|rate+after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Safety",],DAYTOCLOSE~did|rate+factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
+          omit.coef = "after|rate|Intercept", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.coef.names = "DiD effect"
+          )
+
+```
+```{r tab4}
+#ols 
+reg_ols = (lm(data= dat_reg[dat_reg$CATEGORY == "Parks & Recreation",], DAYTOCLOSE~did + rate + after))
+#fe: rate + after
+reg_fe_a = (felm(data = dat_reg[dat_reg$CATEGORY == "Parks & Recreation",],DAYTOCLOSE~did|rate+after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = dat_reg[dat_reg$CATEGORY == "Parks & Recreation",],DAYTOCLOSE~did|rate+factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
+          omit.coef = "after|rate|Intercept", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.coef.names = "DiD effect"
+          )
+
+```
+
+```{r tab1a}
+#ols 
+reg_ols = (lm(data= dat_reg, DAYTOCLOSE~did2 + n_allcovid + after))
+#fe: rate + after
+reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~did2|n_allcovid+after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~did2|n_allcovid+factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
+          omit.coef = "after|n_allcovid|Intercept", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.coef.names = "DiD effect"
+          )
+
+```
+
+```{r tab2a}
+#ols 
+reg_ols = (lm(data= dat_reg[dat_reg$CATEGORY == "Public Health",], DAYTOCLOSE~did2 + n_allcovid + after))
+#fe: rate + after
+reg_fe_a = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Health",],DAYTOCLOSE~did2|n_allcovid+after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Health",],DAYTOCLOSE~did2|n_allcovid+factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
+          omit.coef = "after|n_allcovid|Intercept", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.coef.names = "DiD effect"
+          )
+
+```
+```{r tab3a}
+#ols 
+reg_ols = (lm(data= dat_reg[dat_reg$CATEGORY == "Public Safety",], DAYTOCLOSE~did2 + n_allcovid + after))
+#fe: rate + after
+reg_fe_a = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Safety",],DAYTOCLOSE~did2|n_allcovid+after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Safety",],DAYTOCLOSE~did2|n_allcovid+factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
+          omit.coef = "after|n_allcovid|Intercept", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.coef.names = "DiD effect"
+          )
+
+```
+```{r tab4a}
+#ols 
+reg_ols = (lm(data= dat_reg[dat_reg$CATEGORY == "Parks & Recreation",], DAYTOCLOSE~did2 + n_allcovid + after))
+#fe: rate + after
+reg_fe_a = (felm(data = dat_reg[dat_reg$CATEGORY == "Parks & Recreation",], DAYTOCLOSE~did2|n_allcovid + after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = dat_reg[dat_reg$CATEGORY == "Parks & Recreation",], DAYTOCLOSE~did2|n_allcovid + factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
+          omit.coef = "after|n_allcovid|Intercept", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.coef.names = "DiD effect"
+          )
+
+```
+
+```{r tab5}
+zip_reg = dat %>% 
+  mutate(after = as.numeric(season == "COVID-warm")) %>% 
+  filter(allcovid==0) %>% 
+  #filter(CATEGORY == "Public Health") %>%
+  group_by(date, ZIP, after) %>%
+  summarise(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
+  left_join(zip_covid) %>%
+  left_join(zip_covid_311) %>%
+  mutate(rate = rate*100,
+         did = rate*after,
+         did2 = n_allcovid*after)
+
+#ols 
+reg_ols = (lm(data= zip_reg, DAYTOCLOSE~did + rate + after))
+#fe: rate + after
+reg_fe_a = (felm(data = zip_reg,DAYTOCLOSE~did|rate+after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = zip_reg,DAYTOCLOSE~did|rate+factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
+          omit.coef = "after|rate|Intercept", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.coef.names = "DiD effect"
+          )
+
+```
+
+```{r tab6}
+zip_reg = dat %>% 
+  mutate(after = as.numeric(season == "COVID-warm")) %>% 
+  filter(allcovid==0) %>% 
+  filter(CATEGORY == "Public Health") %>%
+  group_by(date, ZIP, after) %>%
+  summarise(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
+  left_join(zip_covid) %>%
+  left_join(zip_covid_311) %>%
+  mutate(rate = rate*100,
+         did = rate*after,
+         did2 = n_allcovid*after)
+
+#ols 
+reg_ols = (lm(data= zip_reg, DAYTOCLOSE~did + rate + after))
+#fe: rate + after
+reg_fe_a = (felm(data = zip_reg,DAYTOCLOSE~did|rate+after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = zip_reg,DAYTOCLOSE~did|rate+factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
+          omit.coef = "after|rate|Intercept", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.coef.names = "DiD effect"
+          )
+
+```
+```{r tab7}
+zip_reg = dat %>% 
+  mutate(after = as.numeric(season == "COVID-warm")) %>% 
+  filter(allcovid==0) %>% 
+  filter(CATEGORY == "Public Safety") %>%
+  group_by(date, ZIP, after) %>%
+  summarise(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
+  left_join(zip_covid) %>%
+  left_join(zip_covid_311) %>%
+  mutate(rate = rate*100,
+         did = rate*after,
+         did2 = n_allcovid*after)
+
+#ols 
+reg_ols = (lm(data= zip_reg, DAYTOCLOSE~did + rate + after))
+#fe: rate + after
+reg_fe_a = (felm(data = zip_reg,DAYTOCLOSE~did|rate+after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = zip_reg,DAYTOCLOSE~did|rate+factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
+          omit.coef = "after|rate|Intercept", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.coef.names = "DiD effect"
+          )
+
+```
+
+```{r tab8}
+zip_reg = dat %>% 
+  mutate(after = as.numeric(season == "COVID-warm")) %>% 
+  filter(allcovid==0) %>% 
+  filter(CATEGORY == "Parks & Recreation") %>%
+  group_by(date, ZIP, after) %>%
+  summarise(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
+  left_join(zip_covid) %>%
+  left_join(zip_covid_311) %>%
+  mutate(rate = rate*100,
+         did = rate*after,
+         did2 = n_allcovid*after)
+
+#ols 
+reg_ols = (lm(data= zip_reg, DAYTOCLOSE~did + rate + after))
+#fe: rate + after
+reg_fe_a = (felm(data = zip_reg,DAYTOCLOSE~did|rate+after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = zip_reg,DAYTOCLOSE~did|rate+factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
+          omit.coef = "after|rate|Intercept", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.coef.names = "DiD effect"
+          )
+
+```
+
+```{r tab5a}
+zip_reg = dat %>% 
+  mutate(after = as.numeric(season == "COVID-warm")) %>% 
+  filter(allcovid==0) %>% 
+  #filter(CATEGORY == "Public Health") %>%
+  group_by(date, ZIP, after) %>%
+  summarise(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
+  left_join(zip_covid) %>%
+  left_join(zip_covid_311) %>%
+  mutate(rate = rate*100,
+         did = rate*after,
+         did2 = n_allcovid*after)
+
+#ols 
+reg_ols = (lm(data= zip_reg, DAYTOCLOSE~did2 + n_allcovid + after))
+#fe: rate + after
+reg_fe_a = (felm(data = zip_reg,DAYTOCLOSE~did2|n_allcovid+after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = zip_reg,DAYTOCLOSE~did2|n_allcovid+factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
+          omit.coef = "after|n_allcovid|Intercept", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.coef.names = "DiD effect"
+          )
+
+```
+
+```{r tab6a}
+zip_reg = dat %>% 
+  mutate(after = as.numeric(season == "COVID-warm")) %>% 
+  filter(allcovid==0) %>% 
+  filter(CATEGORY == "Public Health") %>%
+  group_by(date, ZIP, after) %>%
+  summarise(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
+  left_join(zip_covid) %>%
+  left_join(zip_covid_311) %>%
+  mutate(rate = rate*100,
+         did = rate*after,
+         did2 = n_allcovid*after)
+
+#ols 
+reg_ols = (lm(data= zip_reg, DAYTOCLOSE~did2 + n_allcovid + after))
+#fe: rate + after
+reg_fe_a = (felm(data = zip_reg,DAYTOCLOSE~did2|n_allcovid+after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = zip_reg,DAYTOCLOSE~did2|n_allcovid+factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
+          omit.coef = "after|n_allcovid|Intercept", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.coef.names = "DiD effect"
+          )
+
+```
+
+```{r tab7a}
+zip_reg = dat %>% 
+  mutate(after = as.numeric(season == "COVID-warm")) %>% 
+  filter(allcovid==0) %>% 
+  filter(CATEGORY == "Public Safety") %>%
+  group_by(date, ZIP, after) %>%
+  summarise(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
+  left_join(zip_covid) %>%
+  left_join(zip_covid_311) %>%
+  mutate(rate = rate*100,
+         did = rate*after,
+         did2 = n_allcovid*after)
+
+#ols 
+reg_ols = (lm(data= zip_reg, DAYTOCLOSE~did2 + n_allcovid + after))
+#fe: rate + after
+reg_fe_a = (felm(data = zip_reg,DAYTOCLOSE~did2|n_allcovid+after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = zip_reg,DAYTOCLOSE~did2|n_allcovid+factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
+          omit.coef = "after|n_allcovid|Intercept", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.coef.names = "DiD effect"
+          )
+
+```
+
+```{r tab8a}
+zip_reg = dat %>% 
+  mutate(after = as.numeric(season == "COVID-warm")) %>% 
+  filter(allcovid==0) %>% 
+  filter(CATEGORY == "Parks & Recreation") %>%
+  group_by(date, ZIP, after) %>%
+  summarise(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
+  left_join(zip_covid) %>%
+  left_join(zip_covid_311) %>%
+  mutate(rate = rate*100,
+         did = rate*after,
+         did2 = n_allcovid*after)
+
+#ols 
+reg_ols = (lm(data= zip_reg, DAYTOCLOSE~did2 + n_allcovid + after))
+#fe: rate + after
+reg_fe_a = (felm(data = zip_reg,DAYTOCLOSE~did2|n_allcovid+after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = zip_reg,DAYTOCLOSE~did2|n_allcovid+factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
+          omit.coef = "after|n_allcovid|Intercept", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.coef.names = "DiD effect"
+          )
+
 ```

### 2022-07-04 README.Rmd
update

@@
   facet_wrap(~CATEGORY, scale = "free_y")+
+  labs(y = "Change in Response Time",x = "COVID-19 infection rate")+
   theme_bw()+
@@
 
+```{r}
+
+zip_covid %>% left_join(zip_covid_311) %>%
+  ggplot(aes(x = rate, y = n_allcovid))+ 
+  geom_point()+
+  geom_smooth(method=lm)+
+  labs(x= "COVID-19 infection rate", y="Volume of covid-related requests")+
+  theme_bw()
+
+```
+
 Discussion

### 2022-07-05 README.Rmd
update

@@
 library(lfe)
+#install.packages("devtools")
+#library(devtools)
+#install_github('arilamstein/choroplethrZip@v1.3.0')
+library(choroplethrZip)
 
@@
   scale_y_continuous(labels =scales::comma)+
-  labs(x = "Requests Volume",
-       y = "Category",
+  labs(y = "Requests Volume",
+       x = "",
        fill = "Year",
@@
 ```
-```{r rep_cat, warning=FALSE, message = FALSE,fig.height = 3,fig.width=8}
+```{r rep_cat, warning=FALSE, message = FALSE,fig.height = 8,fig.width=15}
 # plot response time by categories
 dat %>% 
-  filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
+  filter(CATEGORY != "Data Not Available") %>%
+  #filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
   filter(CREATEMO %in% 3:8) %>%
@@
   mutate(CREATEYR = as.factor(CREATEYR))%>%
+  group_by(CREATEYR, CATEGORY,diff_pchg) %>% summarize(DAYTOCLOSE = mean(DAYTOCLOSE)) %>% 
   ggplot(aes(x = CREATEYR, y = DAYTOCLOSE, fill = CREATEYR))+
-  geom_boxplot(outlier.shape = NA,show.legend = FALSE)+
-  facet_wrap(~reorder(CATEGORY,-diff_pchg), ncol = 3,scale="free")+
+  geom_col(#outlier.shape = NA,
+               show.legend = FALSE)+
+  facet_wrap(~reorder(CATEGORY,-diff_pchg), ncol = 5,scale="free")+
   scale_fill_manual(values = c("dodgerblue4","green3"))+
-  ylim(c(0,80))+
+  #ylim(c(0,80))+
   labs(x = "",
-       y = "Reponse Time",
+       y = "Average Reponse Time",
        fill = "Year",
@@
 
+```{r zip_choropleth}
+
+#list of zip to zoom in
+zip_kcmo = unique(as.character(zip_covid$ZIP))
+
+#zip code choropleth for covid infection rate
+zip_choropleth(zip_covid %>% mutate(region = as.character(ZIP), value = rate*100), 
+               #state_zoom = ec_states, 
+               zip_zoom = zip_kcmo,
+               title      = "",
+               legend     = "COVID-19 Infection Rate") + coord_map()
+
+```
+
 ```{r zip_vol, fig.height = 3,fig.width=8}
-# #scatterplot
-# zip %>% 
-#   ggplot(aes(y = n_diff, x = rate, size = n_2019, col = ZIP))+
-#   geom_point()+
-#   geom_smooth(method=lm)+
-#   facet_wrap(~CATEGORY, scale = "free_y")+
-#   theme_bw()+
-#   theme(legend.position = "none")
+#scatterplot
+zip %>%
+  ggplot(aes(y = n_diff, x = rate, size = n_2019, col = ZIP))+
+  geom_point()+
+  geom_smooth(method=lm)+
+  facet_wrap(~CATEGORY, scale = "free_y")+
+  theme_bw()+
+  theme(legend.position = "none")
 ```

### 2022-07-05 README.Rmd
update

@@
 ```
-```{r rep_cat, warning=FALSE, message = FALSE,fig.height = 8,fig.width=15}
+```{r rep_cat, warning=FALSE, message = FALSE,fig.height = 4,fig.width=6}
 # plot response time by categories
@@
   filter(CATEGORY != "Data Not Available") %>%
-  #filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
   filter(CREATEMO %in% 3:8) %>%
@@
   group_by(CREATEYR, CATEGORY,diff_pchg) %>% summarize(DAYTOCLOSE = mean(DAYTOCLOSE)) %>% 
-  ggplot(aes(x = CREATEYR, y = DAYTOCLOSE, fill = CREATEYR))+
-  geom_col(#outlier.shape = NA,
-               show.legend = FALSE)+
-  facet_wrap(~reorder(CATEGORY,-diff_pchg), ncol = 5,scale="free")+
-  scale_fill_manual(values = c("dodgerblue4","green3"))+
-  #ylim(c(0,80))+
-  labs(x = "",
-       y = "Average Reponse Time",
-       fill = "Year",
-       pattern = "Covid-Related"
+  dcast(CATEGORY+diff_pchg~CREATEYR) %>% mutate(
+    dtc_chg = `2020`-`2019`
+  ) %>%
+  ggplot(aes(x = dtc_chg, y = reorder(CATEGORY,diff_pchg), fill = diff_pchg))+
+  geom_col(show.legend = FALSE)+
+  xlim(c(-10,25))+
+  labs(x = "Change in Average Response Time",
+       y = "",
   )+
@@
 zip_dtc = dat %>% 
-  filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
+  #filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
   filter(CREATEMO %in% 3:8) %>%
@@
 zip_n = dat %>% 
-  filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
+  #filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
   filter(CREATEMO %in% 3:8) %>%
@@
 
-```{r zip_vol, fig.height = 3,fig.width=8}
+Influx of covid-related requests due to COVID-19
+
+```{r}
+# covid related request by zip code 
+zip_covid_311 = dat %>% group_by(ZIP) %>% 
+  summarise(
+    n = n(),
+    n_allcovid = sum(allcovid))
+
+#scatter plot
+zip_covid %>% left_join(zip_covid_311) %>%
+  ggplot(aes(x = rate*100, y = n_allcovid, size = n, col = n))+ 
+  geom_point()+
+  geom_smooth(method=lm)+
+  labs(x= "COVID-19 infection rate", y="Volume of covid-related requests")+
+  theme_bw()+
+  theme(legend.position = "none")
+
+#reg
+summary(lm(rate*100 ~ n_allcovid, 
+           data = zip_covid %>% left_join(zip_covid_311)))
+
+```
+
+```{r zip_vol, fig.height = 8,fig.width=8}
 #scatterplot
@@
 
-```{r zip_dtc, fig.height = 3,fig.width=8}
+Delay in response time for non-covid related requests
+
+```{r zip_dtc, fig.height = 8,fig.width=8}
 #scatter plot
 zip %>% 
-  ggplot(aes(y = daytoclose_diff, x = rate, size = daytoclose_2019, col = ZIP))+
+  #filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
+  ggplot(aes(y = daytoclose_diff, x = rate*100, size = daytoclose_2019, col = ZIP))+
   geom_point()+
@@
 # zip %>% 
+#   filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
 #   ggplot(aes(y = daytoclose_diff, x = n_diff, size = n_2019, col = ZIP))+
@@
 ```{r}
-# covid related request by zip code 
-zip_covid_311 = dat %>% group_by(ZIP) %>% 
-  summarise(n_allcovid = sum(allcovid))
 
@@
 
-```{r}
-
-zip_covid %>% left_join(zip_covid_311) %>%
-  ggplot(aes(x = rate, y = n_allcovid))+ 
-  geom_point()+
-  geom_smooth(method=lm)+
-  labs(x= "COVID-19 infection rate", y="Volume of covid-related requests")+
-  theme_bw()
-
-```
-
 Discussion

### 2022-07-05 README.Rmd
update

@@
 
-```{r zip_dtc, fig.height = 8,fig.width=8}
+```{r zip_dtc, fig.height = 3,fig.width=8}
 #scatter plot
 zip %>% 
-  #filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
+  left_join(diff) %>%
+  filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
   ggplot(aes(y = daytoclose_diff, x = rate*100, size = daytoclose_2019, col = ZIP))+
@@
   geom_smooth(method=lm)+
-  facet_wrap(~CATEGORY, scale = "free_y")+
+  facet_wrap(~reorder(CATEGORY,-diff_pchg), scale = "free_y")+
   labs(y = "Change in Response Time",x = "COVID-19 infection rate")+
@@
           custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"
+          custom.coef.names = "DiD effect"#,
+        #file = "reg.doc"
           )
@@
 reg_fe_b = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Health",],DAYTOCLOSE~did|rate+factor(date) ))
+#fe: nbh + date(year-month)
+#reg_fe_c = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Health",],DAYTOCLOSE~did|factor(NEIGH)+factor(date) ))
 

### 2022-07-14 README.Rmd
update draft

@@
 
+# volume of covid-related of requests
+zip_covid_311 = dat %>%
+  group_by(ZIP) %>% 
+  summarize(n = n(), n_allcovid = sum(allcovid)) %>% na.omit()
+
 #merge data 
 zip = zip_dtc %>% left_join(zip_n) %>%
-  left_join(zip_covid)
+  left_join(zip_covid) %>%
+  left_join(zip_covid_311)
 
@@
 #list of zip to zoom in
-zip_kcmo = unique(as.character(zip_covid$ZIP))
+zip_kcmo = unique(as.character(zip_covid_311$ZIP))
 
-#zip code choropleth for covid infection rate
-zip_choropleth(zip_covid %>% mutate(region = as.character(ZIP), value = rate*100), 
-               #state_zoom = ec_states, 
+#zip code choropleth for 
+zip_choropleth(zip_covid_311 %>% mutate(region = as.character(ZIP), value = n_allcovid), 
                zip_zoom = zip_kcmo,
                title      = "",
-               legend     = "COVID-19 Infection Rate") + coord_map()
+               legend     = "Volume of Covid-related Requests") + coord_map()
 
@@
 
-Influx of covid-related requests due to COVID-19
-
 ```{r}
-# covid related request by zip code 
-zip_covid_311 = dat %>% group_by(ZIP) %>% 
-  summarise(
-    n = n(),
-    n_allcovid = sum(allcovid))
-
-#scatter plot
-zip_covid %>% left_join(zip_covid_311) %>%
-  ggplot(aes(x = rate*100, y = n_allcovid, size = n, col = n))+ 
+#scatterplot
+dat %>% 
+  #filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
+  filter(CREATEMO %in% 3:8) %>%
+  group_by(CREATEYR, ZIP) %>%
+  summarize(daytoclose = mean(DAYTOCLOSE,na.rm=T)) %>%
+  dcast(ZIP ~ CREATEYR) %>% 
+  mutate(daytoclose_diff = `2020`-`2019`)%>% rename(daytoclose_2020 = `2020`,daytoclose_2019=`2019`) %>%
+  left_join(zip_covid_311) %>% 
+  ggplot(aes(y = daytoclose_diff, x = n_allcovid, size = n, col = ZIP))+
   geom_point()+
   geom_smooth(method=lm)+
-  labs(x= "COVID-19 infection rate", y="Volume of covid-related requests")+
   theme_bw()+
@@
 
-#reg
-summary(lm(rate*100 ~ n_allcovid, 
-           data = zip_covid %>% left_join(zip_covid_311)))
+#linear regression
+summary(lm(daytoclose_diff~n_allcovid, data = dat %>% 
+  #filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
+  filter(CREATEMO %in% 3:8) %>%
+  group_by(CREATEYR, ZIP) %>%
+  summarize(daytoclose = mean(DAYTOCLOSE,na.rm=T)) %>%
+  dcast(ZIP ~ CREATEYR) %>% 
+  mutate(daytoclose_diff = `2020`-`2019`)%>% rename(daytoclose_2020 = `2020`,daytoclose_2019=`2019`) %>%
+  left_join(zip_covid_311)
+))
 
@@
 
-```{r zip_vol, fig.height = 8,fig.width=8}
-#scatterplot
-zip %>%
-  ggplot(aes(y = n_diff, x = rate, size = n_2019, col = ZIP))+
-  geom_point()+
-  geom_smooth(method=lm)+
-  facet_wrap(~CATEGORY, scale = "free_y")+
-  theme_bw()+
-  theme(legend.position = "none")
+pretrends
+
+```{r}
+rank10 = zip_covid_311 %>% 
+  mutate(group = cut(zip_covid_311$n_allcovid,breaks = quantile(zip_covid_311$n_allcovid,seq(0,1,0.2)),labels = FALSE,include.lowest = TRUE))
+
+dat %>% left_join(rank10 ) %>% filter(group %in%c(1,5)) %>% 
+  group_by(group,date) %>% 
+  summarise(daytoclose = mean(DAYTOCLOSE,na.rm=T)) %>% 
+  ggplot(aes(x = date, y = daytoclose, group = group, col = as.factor(group)))+
+  geom_line(lwd= 1.5)+
+  theme_bw()
+
 ```
@@
 
-```{r zip_dtc, fig.height = 3,fig.width=8}
-#scatter plot
+```{r zip_dtc, fig.height = 6,fig.width=8}
+#scatterplot
 zip %>%
-  left_join(diff) %>%
-  filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
-  ggplot(aes(y = daytoclose_diff, x = rate*100, size = daytoclose_2019, col = ZIP))+
+  filter(CATEGORY != "Data Not Available") %>%
+  ggplot(aes(y = daytoclose_diff, x = n_allcovid, size = n_2019, col = ZIP))+
   geom_point()+
   geom_smooth(method=lm)+
-  facet_wrap(~reorder(CATEGORY,-diff_pchg), scale = "free_y")+
-  labs(y = "Change in Response Time",x = "COVID-19 infection rate")+
+  facet_wrap(~CATEGORY, scale = "free", ncol=5)+
   theme_bw()+
   theme(legend.position = "none")
-```
-
-```{r zip_dtc2, fig.height = 3,fig.width=8}
-# #scatterplot
-# zip %>% 
-#   filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
-#   ggplot(aes(y = daytoclose_diff, x = n_diff, size = n_2019, col = ZIP))+
-#   geom_point()+
-#   geom_smooth(method=lm)+
-#   facet_wrap(~CATEGORY, scale = "free")+
-#   theme_bw()+
-#   theme(legend.position = "none")
 ```
@@
           custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"#,
-        #file = "reg.doc"
+          custom.coef.names = "DiD effect"
           )

### 2022-07-14 draft_v2.Rmd
update draft

---
title: "Did COVID-19 Induce A Strenuous Effect on the 311 Non-Emergency Services System?"
output: github_document
---

```{r library, warning=FALSE, message = FALSE}
#load library
library(dplyr)
library(reshape2)
library(openxlsx)
library(car)
library(ggplot2)
library(hrbrthemes)
library(viridis)
library(ggpattern)
library(plm)
library(haven)
library(texreg)
library(lfe)
#install.packages("devtools")
#library(devtools)
#install_github('arilamstein/choroplethrZip@v1.3.0')
library(choroplethrZip)

#load 311 data 
load("kcmo2019_2020.rdata")

#load 911 data
dat911 = read.csv("kcmo 911 volume - data.csv")

#All Employees: Government: Local Government in Missouri (SMS29000009093000001)
datgov = read.csv("SMU29281409093000001SA.csv")
names(datgov) = c("datebls","empgov")
datgov$year = as.numeric(substr(datgov$datebls,1,4))
datgov$month = as.numeric(substr(datgov$datebls,6,7))

#covid cases by zipcode as of january 15, 2022
zip_covid = read.csv("COVID-19_Data_by_ZIP_Code.csv") 
zip_covid = zip_covid %>% dplyr::select(ZipCode,Cases,Total.Residents.Tested) %>% mutate(ZIP = ZipCode,rate = Cases/Total.Residents.Tested ) %>% dplyr::select(ZIP, rate)

```

```{r clean, warning=FALSE, message = FALSE}
# create year+month var
dat$date = dat$CREATEYR*100 +dat$CREATEMO

dat$date = as.Date(as.character(dat$date*100+1),"%Y%m%d")

# incomplete requests are imputed with 180 days (close date doen't exist)
#dat$DAYTOCLOSE[dat$DAYTOCLOSE==180] = NA

# create covid related calls 
dat = dat %>%
  mutate(

    covid = as.numeric(grepl("covid",tolower(description))|
                         grepl("corona",tolower(description))|
                         grepl("pandemic",tolower(description))|
                         grepl("virus",tolower(description))|
                         grepl("positive",tolower(description))
    ),

    mask = as.numeric(grepl("mask",tolower(description))|
                        grepl("face cover",tolower(description))|
                        grepl("ppe ",tolower(description))|
                        grepl("coverings",tolower(description))
    ),

    sdistance = as.numeric(grepl("social",tolower(description))|
                             grepl("distanc",tolower(description))|
                             grepl("6 feet",tolower(description))|
                             grepl("quarantine",tolower(description))|
                             grepl("stay at home",tolower(description))|
                             grepl("gathering",tolower(description))
    ),

    essential = as.numeric(grepl("essential",tolower(description))|
                             grepl("still open",tolower(description))|
                             grepl("open for business",tolower(description))|
                             grepl("open and operating",tolower(description))|
                             grepl("still operating",tolower(description))
    ),

    allcovid = as.numeric((covid==1|mask==1|sdistance==1|essential==1) & season == "COVID-warm")
  )
```

supporting dataset

```{r}
# changes in request volume after covid by categories 
diff = dat %>% 
  filter(CATEGORY != "Data Not Available") %>%
  filter(CREATEMO %in% 3:8) %>%
  group_by(CREATEYR,CATEGORY) %>%
  count() %>% 
  dcast(CATEGORY~CREATEYR) %>% 
  mutate(diff = `2020`-`2019`,
         diff_pchg = `2020`/`2019` )
```

Despite the influx of covid-related calls, response time for public health and public safety are actually lower than the previous year

```{r, fig.height=4, fig.width=8}
# plot request volume by categories
dat %>% 
  filter(CATEGORY != "Data Not Available") %>%
  filter(CATEGORY %in% c("Public Safety","Public Health")) %>%
  #filter(CREATEMO %in% 3:8) %>%
  group_by(CREATEYR,date,allcovid,CATEGORY) %>%
  count() %>% 
  left_join(diff)%>%
  mutate(CREATEYR = as.factor(CREATEYR),allcovid = as.factor(allcovid) )%>%
  ggplot(aes(x = date, y = n, fill = reorder(allcovid,-n)))+
  geom_col()+
  facet_wrap(~reorder(CATEGORY,-diff_pchg), scale = "free_y", ncol = 5)+
  scale_fill_manual(values = c("red3","dodgerblue4"))+
  scale_pattern_manual(values=c("stripe","none"))+
  scale_y_continuous(labels =scales::comma)+
  labs(y = "Requests Volume",
       x = "",
       fill = "Covid-Related"
       )+
  theme_bw()
```

```{r, fig.height=4, fig.width=8}
# plot response time by categories
dat %>% 
  filter(CATEGORY != "Data Not Available") %>%
  filter(CATEGORY %in% c("Public Safety","Public Health")) %>%
  #filter(CREATEMO %in% 3:8) %>%
  group_by(CREATEYR,date,allcovid,CATEGORY) %>%
  summarize(n = mean(DAYTOCLOSE,na.rm=T)) %>% 
  left_join(diff)%>%
  mutate(CREATEYR = as.factor(CREATEYR),allcovid = as.factor(allcovid) )%>%
  ggplot(aes(x = date, y = n, fill = reorder(allcovid,-n)))+
  geom_col(position = position_dodge())+
  facet_wrap(~reorder(CATEGORY,-diff_pchg), ncol = 5)+
  scale_fill_manual(values = c("red3","dodgerblue4"))+
  scale_pattern_manual(values=c("stripe","none"))+
  scale_y_continuous(labels =scales::comma)+
  labs(y = "Average Response Time",
       x = "",
       fill = "Covid-Related"
       )+
  theme_bw()
```

```{r}
# plot response time by categories
dat %>% 
  filter(CATEGORY != "Data Not Available") %>%
  filter(CREATEMO %in% 3:8) %>%
  filter(allcovid==0) %>%
  left_join(diff)%>%
  mutate(CREATEYR = as.factor(CREATEYR))%>%
  group_by(CREATEYR, CATEGORY,diff_pchg) %>% 
  summarize(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
  dcast(CATEGORY+diff_pchg~CREATEYR) %>% mutate(
    dtc_chg = `2020`-`2019`
  ) %>%
  ggplot(aes(x = dtc_chg, y = reorder(CATEGORY,diff_pchg), fill = (diff_pchg>1) ))+
  geom_col(show.legend = FALSE)+
  xlim(c(-10,25))+
  scale_fill_manual(values = c("red3","dodgerblue4"))+
  labs(x = "Change in Average Response Time",
       y = "",
  )+
  theme_bw()

```

Method

Geographical variation

```{r zipdata}
# yoy change in days to close
zip_dtc = dat %>% 
  #filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
  filter(CREATEMO %in% 3:8) %>%
  group_by(CREATEYR,CATEGORY, ZIP) %>%
  summarize(daytoclose = mean(DAYTOCLOSE,na.rm=T)) %>%
  dcast(CATEGORY + ZIP ~ CREATEYR) %>% 
  mutate(daytoclose_diff = `2020`-`2019`)%>% rename(daytoclose_2020 = `2020`,daytoclose_2019=`2019`)

# yoy change in volume
zip_n = dat %>% 
  #filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
  filter(CREATEMO %in% 3:8) %>%
  group_by(CREATEYR,CATEGORY, ZIP) %>%
  summarize(n = n()) %>%
  dcast(CATEGORY + ZIP ~ CREATEYR) %>% 
  mutate(n_diff = `2020`-`2019`,
         n_pchg = (`2020` / `2019`-1)*100)  %>% rename(n_2020 = `2020`,n_2019=`2019`)

# volume of covid-related of requests
zip_covid_311 = dat %>%
  group_by(ZIP) %>% 
  summarize(n = n(), n_allcovid = sum(allcovid)) %>% na.omit()

#merge data 
zip = zip_dtc %>% left_join(zip_n) %>%
  left_join(zip_covid) %>%
  left_join(zip_covid_311)

```

```{r zip_choropleth}

#list of zip to zoom in
zip_kcmo = unique(as.character(zip_covid_311$ZIP))

#zip code choropleth for 
zip_choropleth(zip_covid_311 %>% mutate(region = as.character(ZIP), value = n_allcovid), 
               zip_zoom = zip_kcmo,
               title      = "",
               legend     = "Volume of Covid-related Requests") + coord_map()

```

```{r}
#scatterplot
dat %>% 
  #filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
  filter(CREATEMO %in% 3:8) %>%
  group_by(CREATEYR, ZIP) %>%
  summarize(daytoclose = mean(DAYTOCLOSE,na.rm=T)) %>%
  dcast(ZIP ~ CREATEYR) %>% 
  mutate(daytoclose_diff = `2020`-`2019`)%>% rename(daytoclose_2020 = `2020`,daytoclose_2019=`2019`) %>%
  left_join(zip_covid_311) %>% 
  ggplot(aes(y = daytoclose_diff, x = n_allcovid, size = n, col = ZIP))+
  geom_point()+
  geom_smooth(method=lm)+
  labs(
    y = "Change in Average Response Time",
    x = "Volume of Covid-related Requests"
  )+
  theme_bw()+
  theme(legend.position = "none")

#linear regression
summary(lm(daytoclose_diff~n_allcovid, data = dat %>% 
  #filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
  filter(CREATEMO %in% 3:8) %>%
  group_by(CREATEYR, ZIP) %>%
  summarize(daytoclose = mean(DAYTOCLOSE,na.rm=T)) %>%
  dcast(ZIP ~ CREATEYR) %>% 
  mutate(daytoclose_diff = `2020`-`2019`)%>% rename(daytoclose_2020 = `2020`,daytoclose_2019=`2019`) %>%
  left_join(zip_covid_311)
))

```

Difference in difference

state and explain model

Regression results

```{r}
# create data for request level reg
dat_reg = dat %>% 
  filter(allcovid==0) %>%
  left_join(zip_covid_311) %>% 
  mutate(after = as.numeric(season == "COVID-warm"),
         did = n_allcovid*after
         ) %>%  
  left_join(dat911, by=c("CREATEMO" = "month","CREATEYR" = "year")) %>%
  left_join(datgov, by=c("CREATEMO" = "month","CREATEYR" = "year"))

```

```{r}
#ols 
reg_ols = lm(data= dat_reg, DAYTOCLOSE~did + n_allcovid + after)
#fe: rate + after
reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~did|n_allcovid+after ))
#fe: rate + date(year-month)
reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~did|n_allcovid+factor(date) ))
#fe: rate + date(year-month)
reg_fe_c = (felm(data = dat_reg,DAYTOCLOSE~did|factor(NEIGH)+factor(date) ))

#combine reg 
screenreg(list(reg_ols, reg_fe_a, reg_fe_b,reg_fe_c), 
          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
          custom.model.names = c("OLS", "FE period-zipcode", "FE date-zipcode","FE date-neighborhood"),
          custom.coef.names = "DiD effect"
          )
```

```{r}
#fe: rate + after
reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~did|n_allcovid+after ))
#fe: 911
reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~did+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
#fe: gov employees
reg_fe_c = (felm(data = dat_reg,DAYTOCLOSE~did+empgov|n_allcovid+after ))
#fe: 911 + gov employees
reg_fe_d = (felm(data = dat_reg,DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))

#combine reg 
screenreg(list(reg_fe_a, reg_fe_b,reg_fe_c,reg_fe_d), 
          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
          custom.model.names = c("(1)", "(2)","(3)","(4)"),
          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
          )
```

```{r}
#fe: 911 + gov employees
reg_fe_01 = (felm(data = dat_reg[dat_reg$CATEGORY=="Animals / Pets",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_02 = (felm(data = dat_reg[dat_reg$CATEGORY=="Capital Projects",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_03 = (felm(data = dat_reg[dat_reg$CATEGORY=="City Facilities",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_04 = (felm(data = dat_reg[dat_reg$CATEGORY=="Government",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_05 = (felm(data = dat_reg[dat_reg$CATEGORY=="Lights / Signals",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_06 = (felm(data = dat_reg[dat_reg$CATEGORY=="Mowing / Weeds",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_07 = (felm(data = dat_reg[dat_reg$CATEGORY=="Parks & Recreation",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_08 = (felm(data = dat_reg[dat_reg$CATEGORY=="Property / Buildings / Construction",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_09 = (felm(data = dat_reg[dat_reg$CATEGORY=="Public Health",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_10 = (felm(data = dat_reg[dat_reg$CATEGORY=="Public Safety",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_11 = (felm(data = dat_reg[dat_reg$CATEGORY=="Sidewalks / Curbs / Ditch",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_12 = (felm(data = dat_reg[dat_reg$CATEGORY=="Signs",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_13 = (felm(data = dat_reg[dat_reg$CATEGORY=="Storm Water / Sewer",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_14 = (felm(data = dat_reg[dat_reg$CATEGORY=="Streets / Roadways / Alleys",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_15 = (felm(data = dat_reg[dat_reg$CATEGORY=="Trash / Recycling",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))

#combine reg 
screenreg(list(reg_fe_01, reg_fe_02,reg_fe_03,reg_fe_04,reg_fe_05), 
          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
          custom.model.names = c("Animals / Pets", "Capital Projects","City Facilities","Government","Lights / Signals"),
          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
          )

#combine reg 
screenreg(list(reg_fe_06, reg_fe_07,reg_fe_08,reg_fe_09,reg_fe_10), 
          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
          custom.model.names = c("Mowing / Weeds", "Parks & Recreation","Property / Buildings / Construction","Public Health","Public Safety"),
          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
          )

#combine reg 
screenreg(list(reg_fe_11, reg_fe_12,reg_fe_13,reg_fe_14,reg_fe_15), 
          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
          custom.model.names = c("Sidewalks / Curbs / Ditch", "Signs","Storm Water / Sewer","Streets / Roadways / Alleys","Trash / Recycling"),
          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
          )

```

### 2022-07-14 draft_v2.Rmd
update

@@
        )+
+  coord_cartesian(ylim = c(0, 50)) +
+  theme_bw()
+```
+
+```{r,fig.width=15,fig.height=8}
+# plot request volume by categories
+dat %>% 
+  filter(CATEGORY != "Data Not Available") %>%
+  filter(CREATEMO %in% 3:8) %>%
+  group_by(CREATEYR,allcovid,CATEGORY) %>%
+  count() %>% 
+  left_join(diff)%>%
+  mutate(CREATEYR = as.factor(CREATEYR),allcovid = as.factor(allcovid) )%>%
+  ggplot(aes(x = CREATEYR, y = n,  group = reorder(CREATEYR,n), fill = CREATEYR))+
+  geom_col_pattern(aes(pattern = reorder(allcovid,n)),#position = position_dodge(),
+                   col="black",width = 0.8)+
+  facet_wrap(~reorder(CATEGORY,-diff_pchg), scale = "free_y", ncol = 5)+
+  scale_fill_manual(values = c("dodgerblue4","red3"))+
+  scale_pattern_manual(values=c("stripe","none"))+
+  scale_y_continuous(labels =scales::comma)+
+  labs(y = "Requests Volume",
+       x = "",
+       fill = "Year",
+       pattern = "Covid-Related"
+       )+
   theme_bw()
@@
   ) %>%
-  ggplot(aes(x = dtc_chg, y = reorder(CATEGORY,diff_pchg), fill = (diff_pchg>1) ))+
+  ggplot(aes(x = dtc_chg, y = reorder(CATEGORY,diff_pchg), fill = (diff_pchg) ))+
   geom_col(show.legend = FALSE)+
-  xlim(c(-10,25))+
-  scale_fill_manual(values = c("red3","dodgerblue4"))+
+  xlim(c(-10,20))+
+  #scale_fill_manual(values = c("red3","dodgerblue4"))+
   labs(x = "Change in Average Response Time",

### 2022-07-15 draft_v2.Rmd
update

@@
          diff_pchg = `2020`/`2019` )
+```
+summary statistics
+
+```{r}
+#summary stats
+
 ```

### 2022-07-15 draft_v2.Rmd
update

@@
           custom.model.names = c("Sidewalks / Curbs / Ditch", "Signs","Storm Water / Sewer","Streets / Roadways / Alleys","Trash / Recycling"),
+          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees"))
+```
+
+Departments
+
+```{r cate_dept, fig.height=6,fig.width=8}
+dat %>%
+  filter(CATEGORY != "Data Not Available") %>%
+  filter(CREATEMO %in% 3:8) %>%
+  group_by(CATEGORY, DEPT) %>%
+  count() %>%
+  left_join(diff)%>%
+  ggplot(aes(x = reorder(CATEGORY,-diff_pchg), y = DEPT, fill = n))+
+  geom_tile(lwd=1.5)+
+  scale_x_discrete(guide = guide_axis(angle = 90))+
+  labs(
+    y = "Department",
+    x = "Category",
+    fill = "Request Volume",
+    col = "Selected Catgories"
+  )+
+  theme_bw()
+```
+
+```{r}
+#fe: 911 + gov employees
+reg_fe_01 = (felm(data = dat_reg[dat_reg$DEPT=="Aviation",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_02 = (felm(data = dat_reg[dat_reg$DEPT=="City Managers Office",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_03 = (felm(data = dat_reg[dat_reg$DEPT=="City Planning and Development",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+#reg_fe_04 = (felm(data = dat_reg[dat_reg$DEPT=="Convention and Entertainment Center",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_05 = (felm(data = dat_reg[dat_reg$DEPT=="Finance",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_06 = (felm(data = dat_reg[dat_reg$DEPT=="Fire",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_07 = (felm(data = dat_reg[dat_reg$DEPT=="General Service",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_08 = (felm(data = dat_reg[dat_reg$DEPT=="Health",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+#reg_fe_09 = (felm(data = dat_reg[dat_reg$DEPT=="KCPD",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_10 = (felm(data = dat_reg[dat_reg$DEPT=="NHS",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+#reg_fe_11 = (felm(data = dat_reg[dat_reg$DEPT=="Northeast",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_12 = (felm(data = dat_reg[dat_reg$DEPT=="Northland",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_13 = (felm(data = dat_reg[dat_reg$DEPT=="Parks and Rec",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_14 = (felm(data = dat_reg[dat_reg$DEPT=="Public Works",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_15 = (felm(data = dat_reg[dat_reg$DEPT=="South",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_16 = (felm(data = dat_reg[dat_reg$DEPT=="Water Services",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+
+#combine reg 
+screenreg(list(reg_fe_01, reg_fe_02,reg_fe_03,reg_fe_05), 
+          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("Aviation","City Managers Office","City Planning and Development","Finance"),
           custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
@@
 
+#combine reg 
+screenreg(list(reg_fe_06, reg_fe_07,reg_fe_08,reg_fe_10), 
+          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("Fire","General Service","Health","NHS"),
+          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
+          )
+
+#combine reg 
+screenreg(list(reg_fe_12,reg_fe_13,reg_fe_14,reg_fe_15,reg_fe_16), 
+          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("Northland","Parks and Rec","Public Works","South","Water Services"),
+          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees"))
 ```

### 2022-07-17 draft_v2.Rmd
summary stats

@@
 library(choroplethrZip)
+library(kableExtra)
 
@@
 
+#remove data not avail
+dat = dat %>% filter(CATEGORY != "Data Not Available")
 # create covid related calls 
@@
 #summary stats
+ss01 = dat %>% summarize(obs = n(),
+                 min = min(DAYTOCLOSE,na.rm=T),
+                 q25 = quantile(DAYTOCLOSE,0.25,na.rm=T),
+                 mean = mean(DAYTOCLOSE,na.rm=T),
+                 q75 = quantile(DAYTOCLOSE,0.75,na.rm=T),
+                 max = max(DAYTOCLOSE,na.rm=T)
+                 ) %>% mutate(var = "all")
+
+ss02 = dat %>% 
+  group_by(allcovid) %>%
+  summarize(obs = n(),
+                 min = min(DAYTOCLOSE,na.rm=T),
+                 q25 = quantile(DAYTOCLOSE,0.25,na.rm=T),
+                 mean = mean(DAYTOCLOSE,na.rm=T),
+                 q75 = quantile(DAYTOCLOSE,0.75,na.rm=T),
+                 max = max(DAYTOCLOSE,na.rm=T)
+                 ) %>% rename(var = allcovid)
+
+ss03 = dat %>% 
+  group_by(CATEGORY) %>%
+  summarize(obs = n(),
+                 min = min(DAYTOCLOSE,na.rm=T),
+                 q25 = quantile(DAYTOCLOSE,0.25,na.rm=T),
+                 mean = mean(DAYTOCLOSE,na.rm=T),
+                 q75 = quantile(DAYTOCLOSE,0.75,na.rm=T),
+                 max = max(DAYTOCLOSE,na.rm=T)
+                 ) %>% rename(var = CATEGORY)
+
+ss04 = dat %>% 
+  group_by(CREATEYR) %>%
+  summarize(obs = n(),
+                 min = min(DAYTOCLOSE,na.rm=T),
+                 q25 = quantile(DAYTOCLOSE,0.25,na.rm=T),
+                 mean = mean(DAYTOCLOSE,na.rm=T),
+                 q75 = quantile(DAYTOCLOSE,0.75,na.rm=T),
+                 max = max(DAYTOCLOSE,na.rm=T)
+                 ) %>% rename(var = CREATEYR)
+
+ss = rbind(ss01,ss02,ss04,ss03)
+ss
+# ss %>% 
+#   kable() %>%
+#   kable_styling()
 

### 2022-07-17 draft_v2.Rmd
robustness checks

--- 2022-07-15 draft_v2.Rmd
@@
   mutate(after = as.numeric(season == "COVID-warm"),
-         did = n_allcovid*after
+         did = n_allcovid*after,
          ) %>%  
@@
 
-```{r}
-#ols 
-reg_ols = lm(data= dat_reg, DAYTOCLOSE~did + n_allcovid + after)
-#fe: rate + after
-reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~did|n_allcovid+after ))
-#fe: rate + date(year-month)
-reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~did|n_allcovid+factor(date) ))
-#fe: rate + date(year-month)
-reg_fe_c = (felm(data = dat_reg,DAYTOCLOSE~did|factor(NEIGH)+factor(date) ))
-
-#combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b,reg_fe_c), 
-          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
-          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-zipcode", "FE date-zipcode","FE date-neighborhood"),
-          custom.coef.names = "DiD effect"
-          )
-```
+Main results
 
@@
 ```
+
+By Categories
 
@@
           custom.model.names = c("Sidewalks / Curbs / Ditch", "Signs","Storm Water / Sewer","Streets / Roadways / Alleys","Trash / Recycling"),
+          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees"))
+```
+
+Robustness Check
+
+Fixed Effects 
+```{r}
+#ols 
+reg_ols = lm(data= dat_reg, DAYTOCLOSE~did + n_allcovid + after)
+#fe: rate + after
+reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~did|n_allcovid+after ))
+#fe: rate + date(year-month)
+reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~did|n_allcovid+factor(date) ))
+#fe: rate + date(year-month)
+reg_fe_c = (felm(data = dat_reg,DAYTOCLOSE~did|factor(NEIGH)+factor(date) ))
+
+#combine reg 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b,reg_fe_c), 
+          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("OLS", "FE period-zipcode", "FE date-zipcode","FE date-neighborhood"),
+          custom.coef.names = "DiD effect"
+          )
+```
+
+test for difference in pre-period time trends
+
+```{r}
+summary( felm(data= dat_reg, DAYTOCLOSE~n_allcovid:relevel(factor(date),ref=12)|ZIP+factor(date) ))
+```
+
+Placebo test - time:
+move treatment time to before treatment, expect not significant
+
+```{r}
+#create time placebo
+dat_reg = dat_reg %>% 
+  mutate(
+         placebo_after = as.numeric(CREATEYR==2020),
+         placebo_did = n_allcovid*placebo_after,
+         )
+
+#fe: rate + after
+reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~placebo_did|n_allcovid+placebo_after ))
+#fe: 911
+reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~placebo_did+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+placebo_after ))
+#fe: gov employees
+reg_fe_c = (felm(data = dat_reg,DAYTOCLOSE~placebo_did+empgov|n_allcovid+placebo_after ))
+#fe: 911 + gov employees
+reg_fe_d = (felm(data = dat_reg,DAYTOCLOSE~placebo_did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+placebo_after ))
+
+#combine reg 
+screenreg(list(reg_fe_a, reg_fe_b,reg_fe_c,reg_fe_d), 
+          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("(1)", "(2)","(3)","(4)"),
           custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
           )
+```
 
+Placebo test - treatment:
+move treatment effect randomly, expect not significant
+
+```{r}
+#create time placebo
+set.seed(0)
+dat_reg = dat_reg %>% 
+  mutate(
+         placebo_after = as.numeric(CREATEYR==2020),
+         placebo_allcovid = sample(n_allcovid,size = nrow(dat_reg)),
+         placebo_did2 = placebo_allcovid*after,
+         )
+
+#fe: rate + after
+reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~placebo_did2|n_allcovid+after ))
+#fe: 911
+reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~placebo_did2+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+#fe: gov employees
+reg_fe_c = (felm(data = dat_reg,DAYTOCLOSE~placebo_did2+empgov|n_allcovid+after ))
+#fe: 911 + gov employees
+reg_fe_d = (felm(data = dat_reg,DAYTOCLOSE~placebo_did2+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+
+#combine reg 
+screenreg(list(reg_fe_a, reg_fe_b,reg_fe_c,reg_fe_d), 
+          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("(1)", "(2)","(3)","(4)"),
+          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
+          )
 ```

### 2022-07-17 draft_v2.Rmd
test pretrend

@@
 ```{r}
-summary( felm(data= dat_reg, DAYTOCLOSE~n_allcovid:relevel(factor(date),ref=12)|ZIP+factor(date) ))
+#plot coef for pretrend
+library(sjPlot)
+theme_set(theme_sjplot())
+plot_model(lm(data= dat_reg %>% mutate(date = as.factor(date)), DAYTOCLOSE~n_allcovid:relevel(date,ref=11)+n_allcovid+date),
+           vline.color = "black",
+           title="",
+           rm.terms = c("n_allcovid","date [2019-04-01]","date [2019-05-01]","date [2019-06-01]","date [2019-07-01]","date [2019-08-01]","date [2019-09-01]","date [2019-10-01]","date [2019-11-01]","date [2019-12-01]","date [2020-01-01]","date [2020-02-01]","date [2020-03-01]","date [2020-04-01]","date [2020-05-01]","date [2020-06-01]","date [2020-07-01]","date [2020-08-01]"),
+           axis.labels = rev(c("Mar 2019","Apr 2019","May 2019", "Jun 2019","Jul 2019","Aug 2019", "Sep 2019","Oct 2019","Nov 2019","Dec 2019","Feb 2020","Mar 2020","Apr 2020","May 2020", "Jun 2020","Jul 2020","Aug 2020"))
+           )
+
 ```

### 2023-03-26 README.Rmd
Reorganize folder

@@
 
-```{r library, warning=FALSE, message = FALSE}
+```{r setup, warning=FALSE, message = FALSE, include = FALSE}
 #load library
 library(dplyr)
+options(dplyr.summrise.info = FALSE)
 library(reshape2)
@@
 library(choroplethrZip)
+library(mapproj)
 
 #load 311 data 
-load("kcmo2019_2020.rdata")
+load("data/kcmo2019_2020.rdata")
 
 #load 911 data
-dat911 = read.csv("kcmo 911 volume - data.csv")
+dat911 = read.csv("data/kcmo 911 volume - data.csv")
 
 #covid cases by zipcode as of january 15, 2022
-zip_covid = read.csv("COVID-19_Data_by_ZIP_Code.csv") 
+zip_covid = read.csv("data/COVID-19_Data_by_ZIP_Code.csv") 
 zip_covid = zip_covid %>% dplyr::select(ZipCode,Cases,Total.Residents.Tested) %>% mutate(ZIP = ZipCode,rate = Cases/Total.Residents.Tested ) %>% dplyr::select(ZIP, rate)
@@
 
-```{r clean, warning=FALSE, message = FALSE}
+**Abstract**
+
+In this paper we examine whether COVID-19 imposed a crowd out effect on the 311
+non-emergency services using data from Kansas City, Missouri during the early stage of
+the pandemic. Using description text data, we identify covid-related requests and use
+them as a proxy for the strains put on the 311 systems by the health crisis. We find
+robust evidence through our difference in difference approach that zip code with an
+additional covid-related request would experience half an hour delay the response time
+for non-covid related requests. In addition, the strains on the 311 system mainly affected
+three categories: “Mowing / Weeds”, “Trash / Recycling”, and “Animals & Pets”.
+
+Keywords: crisis response, 311, crowd out effect, COVID-19, text mining
+
+```{r clean, warning=FALSE, message = FALSE, echo=FALSE}
 # create year+month var
@@
 
-Aggregate Trends
+### Aggregate Trends
 
@@
 
-```{r vol, warning=FALSE, message = FALSE,fig.width=8}
+```{r vol, warning=FALSE, message = FALSE,fig.width=8, echo=FALSE}
 dat %>% 
@@
 
-```{r vol_cat, warning=FALSE, message = FALSE,fig.width=15,fig.height=8}
+```{r vol_cat, warning=FALSE, message = FALSE,fig.width=15,fig.height=8, echo=FALSE}
 # changes in request volume after covid by categories 
@@
 ```
-```{r rep_cat, warning=FALSE, message = FALSE,fig.height = 4,fig.width=6}
+
+```{r rep_cat, warning=FALSE, message = FALSE,fig.height = 4,fig.width=6, echo=FALSE}
 # plot response time by categories
@@
 
-Zip Code Variation
+### Zip Code Variation
 
-```{r zipdata}
+```{r zipdata, echo=FALSE}
 # yoy change in days to close
@@
 
-```{r zip_choropleth}
+```{r zip_choropleth, echo=FALSE}
 
@@
 
-```{r}
+```{r, echo=FALSE}
 #scatterplot
@@
 
-pretrends
+### Pretrends
 
-```{r}
+```{r, echo=FALSE}
 rank10 = zip_covid_311 %>% 
@@
 
-Delay in response time for non-covid related requests
+### Delay in response time for non-covid related requests
 
-```{r zip_dtc, fig.height = 6,fig.width=8}
+```{r zip_dtc, fig.height = 6,fig.width=8, echo=FALSE}
 #scatterplot
@@
 
-```{r}
+### Regression Output
+
+```{r, echo=FALSE}
 
@@
 
-```{r tab1}
+```{r tab1, echo=FALSE}
 #ols 
@@
 
-```{r tab2}
+```{r tab2, echo=FALSE}
 #ols 
@@
 
-```{r tab3}
+```{r tab3, echo=FALSE}
 #ols 
@@
 ```
-```{r tab4}
+```{r tab4, echo=FALSE}
 #ols 
@@
 
-```{r tab1a}
+```{r tab1a, echo=FALSE}
 #ols 
@@
 
-```{r tab2a}
+```{r tab2a, echo=FALSE}
 #ols 
@@
 ```
-```{r tab3a}
+```{r tab3a, echo=FALSE}
 #ols 
@@
 ```
-```{r tab4a}
+```{r tab4a, echo=FALSE}
 #ols 
@@
 
-```{r tab5}
+```{r tab5, echo=FALSE}
 zip_reg = dat %>% 
@@
 
-```{r tab6}
+```{r tab6, echo=FALSE}
 zip_reg = dat %>% 
@@
 ```
-```{r tab7}
+```{r tab7, echo=FALSE}
 zip_reg = dat %>% 
@@
 
-```{r tab8}
+```{r tab8, echo=FALSE}
 zip_reg = dat %>% 
@@
 
-```{r tab5a}
+```{r tab5a, echo=FALSE}
 zip_reg = dat %>% 
@@
 
-```{r tab6a}
+```{r tab6a, echo=FALSE}
 zip_reg = dat %>% 
@@
 
-```{r tab7a}
+```{r tab7a, echo=FALSE}
 zip_reg = dat %>% 
@@
 
-```{r tab8a}
+```{r tab8a, echo=FALSE}
 zip_reg = dat %>% 
@@
 
-Discussion
+### Discussion
 
@@
 
-```{r cate_dept, fig.height=8,fig.width=8}
+```{r cate_dept, fig.height=8,fig.width=8, echo=FALSE}
 dat %>%
@@
 911 trends
-```{r vol911}
+
+```{r vol911, echo=FALSE}
 
@@
 
-```{r ringtime911}
+```{r ringtime911, echo=FALSE}
 

### 2023-03-26 README.Rmd
Update to most recent version of analysis

@@
 library(dplyr)
-options(dplyr.summrise.info = FALSE)
+options(dplyr.summrise.inform = FALSE)
 library(reshape2)
@@
 library(mapproj)
-
+library(kableExtra)
+library(sjPlot)
 #load 311 data 
@@
 dat911 = read.csv("data/kcmo 911 volume - data.csv")
+
+#All Employees: Government: Local Government in Missouri (SMS29000009093000001)
+datgov = read.csv("data/SMU29281409093000001SA.csv")
+names(datgov) = c("datebls","empgov")
+datgov$year = as.numeric(substr(datgov$datebls,1,4))
+datgov$month = as.numeric(substr(datgov$datebls,6,7))
 
@@
 
+# incomplete requests are imputed with 180 days (close date doen't exist)
+#dat$DAYTOCLOSE[dat$DAYTOCLOSE==180] = NA
+
+#remove data not avail
+dat = dat %>% filter(CATEGORY != "Data Not Available")
 # create covid related calls 
@@
 
-### Aggregate Trends
+supporting dataset
 
-Call Volumes
-
-```{r vol, warning=FALSE, message = FALSE,fig.width=8, echo=FALSE}
-dat %>% 
-  group_by(date,CREATEYR,CREATEMO,allcovid) %>%
-  count() %>% 
-  filter(CREATEMO %in% 3:8) %>%
-  mutate(CREATEYR = as.factor(CREATEYR),allcovid = as.factor(allcovid) )%>%
-  ggplot(aes(x = CREATEMO, y = n,  group = CREATEYR, fill = CREATEYR))+
-  geom_col_pattern(aes(pattern = reorder(allcovid,n)),position = position_dodge(),
-                   col="black",width = 0.8)+
-  scale_fill_manual(values = c("dodgerblue4","green3"))+
-  scale_pattern_manual(values=c("stripe","none"))+
-  scale_x_continuous(breaks = 3:8)+
-  scale_y_continuous(labels =scales::comma)+
-  labs(y = "Requests Volume",
-       x = "Month",
-       fill = "Year",
-       pattern = "Covid-Related"
-       )+
-  theme_bw()
-```
-
-Call Volumes by Request Types
-
-```{r vol_cat, warning=FALSE, message = FALSE,fig.width=15,fig.height=8, echo=FALSE}
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 # changes in request volume after covid by categories 
@@
          diff_pchg = `2020`/`2019` )
+```
 
+## Summary statistics
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#summary stats
+ss01 = dat %>% summarize(obs = n(),
+                 min = min(DAYTOCLOSE,na.rm=T),
+                 q25 = quantile(DAYTOCLOSE,0.25,na.rm=T),
+                 mean = mean(DAYTOCLOSE,na.rm=T),
+                 q75 = quantile(DAYTOCLOSE,0.75,na.rm=T),
+                 max = max(DAYTOCLOSE,na.rm=T)
+                 ) %>% mutate(var = "all")
+
+ss02 = dat %>% 
+  group_by(allcovid) %>%
+  summarize(obs = n(),
+                 min = min(DAYTOCLOSE,na.rm=T),
+                 q25 = quantile(DAYTOCLOSE,0.25,na.rm=T),
+                 mean = mean(DAYTOCLOSE,na.rm=T),
+                 q75 = quantile(DAYTOCLOSE,0.75,na.rm=T),
+                 max = max(DAYTOCLOSE,na.rm=T)
+                 ) %>% rename(var = allcovid)
+
+ss03 = dat %>% 
+  group_by(CATEGORY) %>%
+  summarize(obs = n(),
+                 min = min(DAYTOCLOSE,na.rm=T),
+                 q25 = quantile(DAYTOCLOSE,0.25,na.rm=T),
+                 mean = mean(DAYTOCLOSE,na.rm=T),
+                 q75 = quantile(DAYTOCLOSE,0.75,na.rm=T),
+                 max = max(DAYTOCLOSE,na.rm=T)
+                 ) %>% rename(var = CATEGORY)
+
+ss04 = dat %>% 
+  group_by(CREATEYR) %>%
+  summarize(obs = n(),
+                 min = min(DAYTOCLOSE,na.rm=T),
+                 q25 = quantile(DAYTOCLOSE,0.25,na.rm=T),
+                 mean = mean(DAYTOCLOSE,na.rm=T),
+                 q75 = quantile(DAYTOCLOSE,0.75,na.rm=T),
+                 max = max(DAYTOCLOSE,na.rm=T)
+                 ) %>% rename(var = CREATEYR)
+
+ss = rbind(ss01,ss02,ss04,ss03)
+ss
+# ss %>% 
+#   kable() %>%
+#   kable_styling()
+
+```
+
+Despite the influx of covid-related calls, response time for public health and public safety are actually lower than the previous year
+
+```{r, fig.height=4, fig.width=8, warning=FALSE, message = FALSE, echo=FALSE}
+# plot request volume by categories
+dat %>% 
+  filter(CATEGORY != "Data Not Available") %>%
+  filter(CATEGORY %in% c("Public Safety","Public Health")) %>%
+  #filter(CREATEMO %in% 3:8) %>%
+  group_by(CREATEYR,date,allcovid,CATEGORY) %>%
+  count() %>% 
+  left_join(diff)%>%
+  mutate(CREATEYR = as.factor(CREATEYR),allcovid = as.factor(allcovid) )%>%
+  ggplot(aes(x = date, y = n, fill = reorder(allcovid,-n)))+
+  geom_col()+
+  facet_wrap(~reorder(CATEGORY,-diff_pchg), scale = "free_y", ncol = 5)+
+  scale_fill_manual(values = c("red3","dodgerblue4"))+
+  scale_pattern_manual(values=c("stripe","none"))+
+  scale_y_continuous(labels =scales::comma)+
+  labs(y = "Requests Volume",
+       x = "",
+       fill = "Covid-Related"
+       )+
+  theme_bw()
+```
+
+```{r, fig.height=4, fig.width=8, warning=FALSE, message = FALSE, echo=FALSE}
+# plot response time by categories
+dat %>% 
+  filter(CATEGORY != "Data Not Available") %>%
+  filter(CATEGORY %in% c("Public Safety","Public Health")) %>%
+  #filter(CREATEMO %in% 3:8) %>%
+  group_by(CREATEYR,date,allcovid,CATEGORY) %>%
+  summarize(n = mean(DAYTOCLOSE,na.rm=T)) %>% 
+  left_join(diff)%>%
+  mutate(CREATEYR = as.factor(CREATEYR),allcovid = as.factor(allcovid) )%>%
+  ggplot(aes(x = date, y = n, fill = reorder(allcovid,-n)))+
+  geom_col(position = position_dodge())+
+  facet_wrap(~reorder(CATEGORY,-diff_pchg), ncol = 5)+
+  scale_fill_manual(values = c("red3","dodgerblue4"))+
+  scale_pattern_manual(values=c("stripe","none"))+
+  scale_y_continuous(labels =scales::comma)+
+  labs(y = "Average Response Time",
+       x = "",
+       fill = "Covid-Related"
+       )+
+  coord_cartesian(ylim = c(0, 50)) +
+  theme_bw()
+```
+
+```{r,fig.width=15,fig.height=8, warning=FALSE, message = FALSE, echo=FALSE}
 # plot request volume by categories
@@
   facet_wrap(~reorder(CATEGORY,-diff_pchg), scale = "free_y", ncol = 5)+
-  scale_fill_manual(values = c("dodgerblue4","green3"))+
+  scale_fill_manual(values = c("dodgerblue4","red3"))+
   scale_pattern_manual(values=c("stripe","none"))+
@@
 
-```{r rep_cat, warning=FALSE, message = FALSE,fig.height = 4,fig.width=6, echo=FALSE}
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 # plot response time by categories
@@
   mutate(CREATEYR = as.factor(CREATEYR))%>%
-  group_by(CREATEYR, CATEGORY,diff_pchg) %>% summarize(DAYTOCLOSE = mean(DAYTOCLOSE)) %>% 
+  group_by(CREATEYR, CATEGORY,diff_pchg) %>% 
+  summarize(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
   dcast(CATEGORY+diff_pchg~CREATEYR) %>% mutate(
@@
   ) %>%
-  ggplot(aes(x = dtc_chg, y = reorder(CATEGORY,diff_pchg), fill = diff_pchg))+
+  ggplot(aes(x = dtc_chg, y = reorder(CATEGORY,diff_pchg), fill = (diff_pchg) ))+
   geom_col(show.legend = FALSE)+
-  xlim(c(-10,25))+
+  xlim(c(-10,20))+
+  #scale_fill_manual(values = c("red3","dodgerblue4"))+
   labs(x = "Change in Average Response Time",
@@
   theme_bw()
+
 ```
 
-### Zip Code Variation
+## Method
 
-```{r zipdata, echo=FALSE}
+### Geographical variation
+
+```{r zipdata, warning=FALSE, message = FALSE, echo=FALSE}
 # yoy change in days to close
@@
 
-```{r zip_choropleth, echo=FALSE}
+```{r zip_choropleth, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
 
-```{r, echo=FALSE}
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 #scatterplot
@@
   geom_smooth(method=lm)+
+  labs(
+    y = "Change in Average Response Time",
+    x = "Volume of Covid-related Requests"
+  )+
   theme_bw()+
@@
 
-### Pretrends
+## Difference in difference
 
-```{r, echo=FALSE}
-rank10 = zip_covid_311 %>% 
-  mutate(group = cut(zip_covid_311$n_allcovid,breaks = quantile(zip_covid_311$n_allcovid,seq(0,1,0.2)),labels = FALSE,include.lowest = TRUE))
+### Regression results
 
-dat %>% left_join(rank10 ) %>% filter(group %in%c(1,5)) %>% 
-  group_by(group,date) %>% 
-  summarise(daytoclose = mean(DAYTOCLOSE,na.rm=T)) %>% 
-  ggplot(aes(x = date, y = daytoclose, group = group, col = as.factor(group)))+
-  geom_line(lwd= 1.5)+
-  theme_bw()
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# create data for request level reg
+dat_reg = dat %>% 
+  filter(allcovid==0) %>%
+  left_join(zip_covid_311) %>% 
+  mutate(after = as.numeric(season == "COVID-warm"),
+         did = n_allcovid*after,
+         ) %>%  
+  left_join(dat911, by=c("CREATEMO" = "month","CREATEYR" = "year")) %>%
+  left_join(datgov, by=c("CREATEMO" = "month","CREATEYR" = "year"))
 
@@
 
-### Delay in response time for non-covid related requests
+### Main results
 
-```{r zip_dtc, fig.height = 6,fig.width=8, echo=FALSE}
-#scatterplot
-zip %>%
-  filter(CATEGORY != "Data Not Available") %>%
-  ggplot(aes(y = daytoclose_diff, x = n_allcovid, size = n_2019, col = ZIP))+
-  geom_point()+
-  geom_smooth(method=lm)+
-  facet_wrap(~CATEGORY, scale = "free", ncol=5)+
-  theme_bw()+
-  theme(legend.position = "none")
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#fe: rate + after
+reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~did|n_allcovid+after ))
+#fe: 911
+reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~did+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+#fe: gov employees
+reg_fe_c = (felm(data = dat_reg,DAYTOCLOSE~did+empgov|n_allcovid+after ))
+#fe: 911 + gov employees
+reg_fe_d = (felm(data = dat_reg,DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+
+#combine reg 
+screenreg(list(reg_fe_a, reg_fe_b,reg_fe_c,reg_fe_d), 
+          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("(1)", "(2)","(3)","(4)"),
+          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
+          )
 ```
 
-### Regression Output
+### By Categories
 
-```{r, echo=FALSE}
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#fe: 911 + gov employees
+reg_fe_01 = (felm(data = dat_reg[dat_reg$CATEGORY=="Animals / Pets",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_02 = (felm(data = dat_reg[dat_reg$CATEGORY=="Capital Projects",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_03 = (felm(data = dat_reg[dat_reg$CATEGORY=="City Facilities",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_04 = (felm(data = dat_reg[dat_reg$CATEGORY=="Government",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_05 = (felm(data = dat_reg[dat_reg$CATEGORY=="Lights / Signals",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_06 = (felm(data = dat_reg[dat_reg$CATEGORY=="Mowing / Weeds",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_07 = (felm(data = dat_reg[dat_reg$CATEGORY=="Parks & Recreation",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_08 = (felm(data = dat_reg[dat_reg$CATEGORY=="Property / Buildings / Construction",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_09 = (felm(data = dat_reg[dat_reg$CATEGORY=="Public Health",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_10 = (felm(data = dat_reg[dat_reg$CATEGORY=="Public Safety",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_11 = (felm(data = dat_reg[dat_reg$CATEGORY=="Sidewalks / Curbs / Ditch",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_12 = (felm(data = dat_reg[dat_reg$CATEGORY=="Signs",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_13 = (felm(data = dat_reg[dat_reg$CATEGORY=="Storm Water / Sewer",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_14 = (felm(data = dat_reg[dat_reg$CATEGORY=="Streets / Roadways / Alleys",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+reg_fe_15 = (felm(data = dat_reg[dat_reg$CATEGORY=="Trash / Recycling",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
 
-# create data for request level reg
-dat_reg = dat %>% 
-  left_join(zip_covid) %>%
-  left_join(zip_covid_311) %>% 
-  mutate(after = as.numeric(season == "COVID-warm"),
-         rate = rate*100) %>% 
-  filter(allcovid==0) %>% 
-  mutate(did = rate*after,
-         did2 = n_allcovid*after)
+#combine reg 
+screenreg(list(reg_fe_01, reg_fe_02,reg_fe_03,reg_fe_04,reg_fe_05), 
+          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("Animals / Pets", "Capital Projects","City Facilities","Government","Lights / Signals"),
+          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
+          )
 
+#combine reg 
+screenreg(list(reg_fe_06, reg_fe_07,reg_fe_08,reg_fe_09,reg_fe_10), 
+          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("Mowing / Weeds", "Parks & Recreation","Property / Buildings / Construction","Public Health","Public Safety"),
+          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
+          )
+
+#combine reg 
+screenreg(list(reg_fe_11, reg_fe_12,reg_fe_13,reg_fe_14,reg_fe_15), 
+          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
+          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
+          custom.model.names = c("Sidewalks / Curbs / Ditch", "Signs","Storm Water / Sewer","Streets / Roadways / Alleys","Trash / Recycling"),
+          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees"))
 ```
 
-```{r tab1, echo=FALSE}
+## Robustness Check
+
+### Fixed Effects
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 #ols 
-reg_ols = (lm(data= dat_reg, DAYTOCLOSE~did + rate + after))
+reg_ols = lm(data= dat_reg, DAYTOCLOSE~did + n_allcovid + after)
 #fe: rate + after
-reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~did|rate+after ))
+reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~did|n_allcovid+after ))
 #fe: rate + date(year-month)
-reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~did|rate+factor(date) ))
+reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~did|n_allcovid+factor(date) ))
+#fe: rate + date(year-month)
+reg_fe_c = (felm(data = dat_reg,DAYTOCLOSE~did|factor(NEIGH)+factor(date) ))
 
 #combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
-          omit.coef = "after|rate|Intercept", digits=4, 
+screenreg(list(reg_ols, reg_fe_a, reg_fe_b,reg_fe_c), 
+          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
           include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
+          custom.model.names = c("OLS", "FE period-zipcode", "FE date-zipcode","FE date-neighborhood"),
           custom.coef.names = "DiD effect"
+          )
+```
+
+### Test for difference in pre-period time trends
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#plot coef for pretrend
+theme_set(theme_sjplot())
+plot_model(lm(data= dat_reg %>% mutate(date = as.factor(date)), DAYTOCLOSE~n_allcovid:relevel(date,ref=11)+n_allcovid+date),
+           vline.color = "black",
+           title="",
+           rm.terms = c("n_allcovid","date [2019-04-01]","date [2019-05-01]","date [2019-06-01]","date [2019-07-01]","date [2019-08-01]","date [2019-09-01]","date [2019-10-01]","date [2019-11-01]","date [2019-12-01]","date [2020-01-01]","date [2020-02-01]","date [2020-03-01]","date [2020-04-01]","date [2020-05-01]","date [2020-06-01]","date [2020-07-01]","date [2020-08-01]"),
+           axis.labels = rev(c("Mar 2019","Apr 2019","May 2019", "Jun 2019","Jul 2019","Aug 2019", "Sep 2019","Oct 2019","Nov 2019","Dec 2019","Feb 2020","Mar 2020","Apr 2020","May 2020", "Jun 2020","Jul 2020","Aug 2020"))
            )
@@
 
-```{r tab2, echo=FALSE}
-#ols 
-reg_ols = (lm(data= dat_reg[dat_reg$CATEGORY == "Public Health",], DAYTOCLOSE~did + rate + after))
+### Placebo test - time:
+
+Move treatment time to before treatment, expect not significant
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#create time placebo
+dat_reg = dat_reg %>% 
+  mutate(
+         placebo_after = as.numeric(CREATEYR==2020),
+         placebo_did = n_allcovid*placebo_after,
+         )
+
 #fe: rate + after
-reg_fe_a = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Health",],DAYTOCLOSE~did|rate+after ))
-#fe: rate + date(year-month)
-reg_fe_b = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Health",],DAYTOCLOSE~did|rate+factor(date) ))
-#fe: nbh + date(year-month)
-#reg_fe_c = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Health",],DAYTOCLOSE~did|factor(NEIGH)+factor(date) ))
+reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~placebo_did|n_allcovid+placebo_after ))
+#fe: 911
+reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~placebo_did+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+placebo_after ))
+#fe: gov employees
+reg_fe_c = (felm(data = dat_reg,DAYTOCLOSE~placebo_did+empgov|n_allcovid+placebo_after ))
+#fe: 911 + gov employees
+reg_fe_d = (felm(data = dat_reg,DAYTOCLOSE~placebo_did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+placebo_after ))
 
 #combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
-          omit.coef = "after|rate|Intercept", digits=4, 
+screenreg(list(reg_fe_a, reg_fe_b,reg_fe_c,reg_fe_d), 
+          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
           include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"
+          custom.model.names = c("(1)", "(2)","(3)","(4)"),
+          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
+          )
+```
+
+### Placebo test - treatment:
+
+Move treatment effect randomly, expect not significant
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#create time placebo
+set.seed(0)
+dat_reg = dat_reg %>% 
+  mutate(
+         placebo_after = as.numeric(CREATEYR==2020),
+         placebo_allcovid = sample(n_allcovid,size = nrow(dat_reg)),
+         placebo_did2 = placebo_allcovid*after,
          )
 
-```
-
-```{r tab3, echo=FALSE}
-#ols 
-reg_ols = (lm(data= dat_reg[dat_reg$CATEGORY == "Public Safety",], DAYTOCLOSE~did + rate + after))
 #fe: rate + after
-reg_fe_a = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Safety",],DAYTOCLOSE~did|rate+after ))
-#fe: rate + date(year-month)
-reg_fe_b = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Safety",],DAYTOCLOSE~did|rate+factor(date) ))
+reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~placebo_did2|n_allcovid+after ))
+#fe: 911
+reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~placebo_did2+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
+#fe: gov employees
+reg_fe_c = (felm(data = dat_reg,DAYTOCLOSE~placebo_did2+empgov|n_allcovid+after ))
+#fe: 911 + gov employees
+reg_fe_d = (felm(data = dat_reg,DAYTOCLOSE~placebo_did2+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
 
 #combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
-          omit.coef = "after|rate|Intercept", digits=4, 
+screenreg(list(reg_fe_a, reg_fe_b,reg_fe_c,reg_fe_d), 
+          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
           include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"
+          custom.model.names = c("(1)", "(2)","(3)","(4)"),
+          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
           )
-
 ```
-```{r tab4, echo=FALSE}
-#ols 
-reg_ols = (lm(data= dat_reg[dat_reg$CATEGORY == "Parks & Recreation",], DAYTOCLOSE~did + rate + after))
-#fe: rate + after
-reg_fe_a = (felm(data = dat_reg[dat_reg$CATEGORY == "Parks & Recreation",],DAYTOCLOSE~did|rate+after ))
-#fe: rate + date(year-month)
-reg_fe_b = (felm(data = dat_reg[dat_reg$CATEGORY == "Parks & Recreation",],DAYTOCLOSE~did|rate+factor(date) ))
-
-#combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
-          omit.coef = "after|rate|Intercept", digits=4, 
-          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"
-          )
-
-```
-
-```{r tab1a, echo=FALSE}
-#ols 
-reg_ols = (lm(data= dat_reg, DAYTOCLOSE~did2 + n_allcovid + after))
-#fe: rate + after
-reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~did2|n_allcovid+after ))
-#fe: rate + date(year-month)
-reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~did2|n_allcovid+factor(date) ))
-
-#combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
-          omit.coef = "after|n_allcovid|Intercept", digits=4, 
-          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"
-          )
-
-```
-
-```{r tab2a, echo=FALSE}
-#ols 
-reg_ols = (lm(data= dat_reg[dat_reg$CATEGORY == "Public Health",], DAYTOCLOSE~did2 + n_allcovid + after))
-#fe: rate + after
-reg_fe_a = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Health",],DAYTOCLOSE~did2|n_allcovid+after ))
-#fe: rate + date(year-month)
-reg_fe_b = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Health",],DAYTOCLOSE~did2|n_allcovid+factor(date) ))
-
-#combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
-          omit.coef = "after|n_allcovid|Intercept", digits=4, 
-          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"
-          )
-
-```
-```{r tab3a, echo=FALSE}
-#ols 
-reg_ols = (lm(data= dat_reg[dat_reg$CATEGORY == "Public Safety",], DAYTOCLOSE~did2 + n_allcovid + after))
-#fe: rate + after
-reg_fe_a = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Safety",],DAYTOCLOSE~did2|n_allcovid+after ))
-#fe: rate + date(year-month)
-reg_fe_b = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Safety",],DAYTOCLOSE~did2|n_allcovid+factor(date) ))
-
-#combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
-          omit.coef = "after|n_allcovid|Intercept", digits=4, 
-          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"
-          )
-
-```
-```{r tab4a, echo=FALSE}
-#ols 
-reg_ols = (lm(data= dat_reg[dat_reg$CATEGORY == "Parks & Recreation",], DAYTOCLOSE~did2 + n_allcovid + after))
-#fe: rate + after
-reg_fe_a = (felm(data = dat_reg[dat_reg$CATEGORY == "Parks & Recreation",], DAYTOCLOSE~did2|n_allcovid + after ))
-#fe: rate + date(year-month)
-reg_fe_b = (felm(data = dat_reg[dat_reg$CATEGORY == "Parks & Recreation",], DAYTOCLOSE~did2|n_allcovid + factor(date) ))
-
-#combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
-          omit.coef = "after|n_allcovid|Intercept", digits=4, 
-          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"
-          )
-
-```
-
-```{r tab5, echo=FALSE}
-zip_reg = dat %>% 
-  mutate(after = as.numeric(season == "COVID-warm")) %>% 
-  filter(allcovid==0) %>% 
-  #filter(CATEGORY == "Public Health") %>%
-  group_by(date, ZIP, after) %>%
-  summarise(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
-  left_join(zip_covid) %>%
-  left_join(zip_covid_311) %>%
-  mutate(rate = rate*100,
-         did = rate*after,
-         did2 = n_allcovid*after)
-
-#ols 
-reg_ols = (lm(data= zip_reg, DAYTOCLOSE~did + rate + after))
-#fe: rate + after
-reg_fe_a = (felm(data = zip_reg,DAYTOCLOSE~did|rate+after ))
-#fe: rate + date(year-month)
-reg_fe_b = (felm(data = zip_reg,DAYTOCLOSE~did|rate+factor(date) ))
-
-#combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
-          omit.coef = "after|rate|Intercept", digits=4, 
-          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"
-          )
-
-```
-
-```{r tab6, echo=FALSE}
-zip_reg = dat %>% 
-  mutate(after = as.numeric(season == "COVID-warm")) %>% 
-  filter(allcovid==0) %>% 
-  filter(CATEGORY == "Public Health") %>%
-  group_by(date, ZIP, after) %>%
-  summarise(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
-  left_join(zip_covid) %>%
-  left_join(zip_covid_311) %>%
-  mutate(rate = rate*100,
-         did = rate*after,
-         did2 = n_allcovid*after)
-
-#ols 
-reg_ols = (lm(data= zip_reg, DAYTOCLOSE~did + rate + after))
-#fe: rate + after
-reg_fe_a = (felm(data = zip_reg,DAYTOCLOSE~did|rate+after ))
-#fe: rate + date(year-month)
-reg_fe_b = (felm(data = zip_reg,DAYTOCLOSE~did|rate+factor(date) ))
-
-#combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
-          omit.coef = "after|rate|Intercept", digits=4, 
-          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"
-          )
-
-```
-```{r tab7, echo=FALSE}
-zip_reg = dat %>% 
-  mutate(after = as.numeric(season == "COVID-warm")) %>% 
-  filter(allcovid==0) %>% 
-  filter(CATEGORY == "Public Safety") %>%
-  group_by(date, ZIP, after) %>%
-  summarise(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
-  left_join(zip_covid) %>%
-  left_join(zip_covid_311) %>%
-  mutate(rate = rate*100,
-         did = rate*after,
-         did2 = n_allcovid*after)
-
-#ols 
-reg_ols = (lm(data= zip_reg, DAYTOCLOSE~did + rate + after))
-#fe: rate + after
-reg_fe_a = (felm(data = zip_reg,DAYTOCLOSE~did|rate+after ))
-#fe: rate + date(year-month)
-reg_fe_b = (felm(data = zip_reg,DAYTOCLOSE~did|rate+factor(date) ))
-
-#combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
-          omit.coef = "after|rate|Intercept", digits=4, 
-          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"
-          )
-
-```
-
-```{r tab8, echo=FALSE}
-zip_reg = dat %>% 
-  mutate(after = as.numeric(season == "COVID-warm")) %>% 
-  filter(allcovid==0) %>% 
-  filter(CATEGORY == "Parks & Recreation") %>%
-  group_by(date, ZIP, after) %>%
-  summarise(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
-  left_join(zip_covid) %>%
-  left_join(zip_covid_311) %>%
-  mutate(rate = rate*100,
-         did = rate*after,
-         did2 = n_allcovid*after)
-
-#ols 
-reg_ols = (lm(data= zip_reg, DAYTOCLOSE~did + rate + after))
-#fe: rate + after
-reg_fe_a = (felm(data = zip_reg,DAYTOCLOSE~did|rate+after ))
-#fe: rate + date(year-month)
-reg_fe_b = (felm(data = zip_reg,DAYTOCLOSE~did|rate+factor(date) ))
-
-#combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
-          omit.coef = "after|rate|Intercept", digits=4, 
-          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"
-          )
-
-```
-
-```{r tab5a, echo=FALSE}
-zip_reg = dat %>% 
-  mutate(after = as.numeric(season == "COVID-warm")) %>% 
-  filter(allcovid==0) %>% 
-  #filter(CATEGORY == "Public Health") %>%
-  group_by(date, ZIP, after) %>%
-  summarise(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
-  left_join(zip_covid) %>%
-  left_join(zip_covid_311) %>%
-  mutate(rate = rate*100,
-         did = rate*after,
-         did2 = n_allcovid*after)
-
-#ols 
-reg_ols = (lm(data= zip_reg, DAYTOCLOSE~did2 + n_allcovid + after))
-#fe: rate + after
-reg_fe_a = (felm(data = zip_reg,DAYTOCLOSE~did2|n_allcovid+after ))
-#fe: rate + date(year-month)
-reg_fe_b = (felm(data = zip_reg,DAYTOCLOSE~did2|n_allcovid+factor(date) ))
-
-#combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
-          omit.coef = "after|n_allcovid|Intercept", digits=4, 
-          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"
-          )
-
-```
-
-```{r tab6a, echo=FALSE}
-zip_reg = dat %>% 
-  mutate(after = as.numeric(season == "COVID-warm")) %>% 
-  filter(allcovid==0) %>% 
-  filter(CATEGORY == "Public Health") %>%
-  group_by(date, ZIP, after) %>%
-  summarise(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
-  left_join(zip_covid) %>%
-  left_join(zip_covid_311) %>%
-  mutate(rate = rate*100,
-         did = rate*after,
-         did2 = n_allcovid*after)
-
-#ols 
-reg_ols = (lm(data= zip_reg, DAYTOCLOSE~did2 + n_allcovid + after))
-#fe: rate + after
-reg_fe_a = (felm(data = zip_reg,DAYTOCLOSE~did2|n_allcovid+after ))
-#fe: rate + date(year-month)
-reg_fe_b = (felm(data = zip_reg,DAYTOCLOSE~did2|n_allcovid+factor(date) ))
-
-#combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
-          omit.coef = "after|n_allcovid|Intercept", digits=4, 
-          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"
-          )
-
-```
-
-```{r tab7a, echo=FALSE}
-zip_reg = dat %>% 
-  mutate(after = as.numeric(season == "COVID-warm")) %>% 
-  filter(allcovid==0) %>% 
-  filter(CATEGORY == "Public Safety") %>%
-  group_by(date, ZIP, after) %>%
-  summarise(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
-  left_join(zip_covid) %>%
-  left_join(zip_covid_311) %>%
-  mutate(rate = rate*100,
-         did = rate*after,
-         did2 = n_allcovid*after)
-
-#ols 
-reg_ols = (lm(data= zip_reg, DAYTOCLOSE~did2 + n_allcovid + after))
-#fe: rate + after
-reg_fe_a = (felm(data = zip_reg,DAYTOCLOSE~did2|n_allcovid+after ))
-#fe: rate + date(year-month)
-reg_fe_b = (felm(data = zip_reg,DAYTOCLOSE~did2|n_allcovid+factor(date) ))
-
-#combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
-          omit.coef = "after|n_allcovid|Intercept", digits=4, 
-          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"
-          )
-
-```
-
-```{r tab8a, echo=FALSE}
-zip_reg = dat %>% 
-  mutate(after = as.numeric(season == "COVID-warm")) %>% 
-  filter(allcovid==0) %>% 
-  filter(CATEGORY == "Parks & Recreation") %>%
-  group_by(date, ZIP, after) %>%
-  summarise(DAYTOCLOSE = mean(DAYTOCLOSE,na.rm=T)) %>% 
-  left_join(zip_covid) %>%
-  left_join(zip_covid_311) %>%
-  mutate(rate = rate*100,
-         did = rate*after,
-         did2 = n_allcovid*after)
-
-#ols 
-reg_ols = (lm(data= zip_reg, DAYTOCLOSE~did2 + n_allcovid + after))
-#fe: rate + after
-reg_fe_a = (felm(data = zip_reg,DAYTOCLOSE~did2|n_allcovid+after ))
-#fe: rate + date(year-month)
-reg_fe_b = (felm(data = zip_reg,DAYTOCLOSE~did2|n_allcovid+factor(date) ))
-
-#combine reg 
-screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
-          omit.coef = "after|n_allcovid|Intercept", digits=4, 
-          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
-          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
-          custom.coef.names = "DiD effect"
-          )
-
-```
-
-### Discussion
-
-Categories vs Departments
-
-```{r cate_dept, fig.height=8,fig.width=8, echo=FALSE}
-dat %>%
-  filter(CATEGORY != "Data Not Available") %>%
-  filter(CREATEMO %in% 3:8) %>%
-  group_by(CATEGORY, DEPT) %>%
-  count() %>%
-  left_join(diff)%>%
-  mutate(selected = CATEGORY %in% c("Public Health","Public Safety","Parks & Recreation"))%>%
-  ggplot(aes(x = reorder(CATEGORY,-diff_pchg), y = DEPT, fill = n, col = selected))+
-  geom_tile(lwd=1.5)+
-  scale_x_discrete(guide = guide_axis(angle = 90))+
-  scale_color_manual(values=c("white","red"))+
-  labs(
-    y = "Department",
-    x = "Category",
-    fill = "Request Volume",
-    col = "Selected Catgories"
-  )+
-  theme_bw()
-```
-
-911 trends
-
-```{r vol911, echo=FALSE}
-
-dat911 %>% 
-  filter(month %in% 3:8) %>%
-  mutate(year = as.factor(year)) %>%
-  select(year, month, 
-         kcmo_fire_vol,kcmo_fire_vol_911,kcmo_fire_vol_nonemergency,
-         kcmo_pd_vol,kcmo_pd_vol_911,kcmo_pd_vol_nonemergency) %>%
-  melt(id.vars=c("year","month")) %>%
-  ggplot(aes(x = year, y = value, group = year, fill = year)) + 
-  geom_boxplot(show.legend=FALSE)+
-  facet_wrap(~variable,scale="free_y")+
-  scale_fill_manual(values = c("dodgerblue4","green3"))+
-  #scale_x_continuous(breaks = 3:8)+
-  scale_y_continuous(labels =scales::comma)+
-  labs(y = "911 Volume",
-       x = "Month",
-       fill = "Year"
-       )+
-  theme_bw()
-```
-
-```{r ringtime911, echo=FALSE}
-
-dat911 %>% 
-  filter(month %in% 3:8) %>%
-  mutate(year = as.factor(year)) %>%
-  select(year, month, 
-         kcmo_fire_pct_answered_15s,kcmo_fire_pct_answered_20s,kcmo_fire_pct_answered_40s,
-         kcmo_pd_pct_answered_15s,kcmo_pd_pct_answered_20s,kcmo_pd_pct_answered_40s) %>%
-  melt(id.vars=c("year","month")) %>%
-  ggplot(aes(x = year, y = value, group = year, fill = year)) + 
-  geom_boxplot(show.legend=FALSE)+
-  facet_wrap(~variable,scale="free_y")+
-  scale_fill_manual(values = c("dodgerblue4","green3"))+
-  labs(y = "911 Ringtime Range",
-       x = "",
-       fill = "Year"
-       )+
-  theme_bw()
-```
